---
title: "simulation_mixed_effect_model"
output:
  pdf_document: default
  html_document: default
---

Setting up a multi-level model for simulated data
Idea
  For each examiner–cset response, generate: 1) p_inconclusive . 2) $I_{ij} \sim Bernoulli(p_{ij}^{(I)})$
  
  $$
  p_{ij}^{(I)}=\alpha_0 + \alpha_Ddj+\alpha_Ssi+\alpha_Qqj+\alpha_HH+u_i^{(I)}+v_j^{(I)}+e_{ij}^{(I)}
  $$
  
  $\alpha_0$:the baseline error rate
  $\alpha_D$: $\alpha_D \gt 0$ harder csets increase error
  $\alpha_S$: $\alpha_S \lt 0$ more skilled examiners reduce error
  $\alpha_Q$: $\alpha_Q  \lt 0$ better quality reduce error 
  $\alpha_H$: $\alpha_Q  \gt 0$ Hawthrone effect on increase the inconslusives
  $u_i\sim N(0,\sigma^2_{exam})$: some examiners are systematically more error-prone
  $u_j\sim N(0,\sigma^2_{exam})$: some csets are systematically more error-prone
  $e_{ij} \sim N(0,\sigma^2)$: extra noise
  Then, only for rows that are not inconclusive, generate:1) p_error 2)$E_{ij}|I_{ij} \sim Bernoulli(p_{ij}^{(E)})$
    $$
  p_{ij}^{(E)}=\beta_0 + \beta_Ddj+\beta_Ssi+\beta_Qqj+\beta_HH+u_i^{(E)}+v_j^{(E)}+e_{ij}^{(E)}
    $$
    $\alpha_0$:the baseline error rate
  $\alpha_D$: $\alpha_D \gt 0$ harder csets increase inconslusives
  $\alpha_S$: $\alpha_S \lt 0$ more skilled examiners reduce inconslusives
  $\alpha_Q$: $\alpha_Q  \lt 0$ better quality reduce inconslusives 
  $u_i\sim N(0,\sigma^2_{exam})$: some examiners are systematically more inconslusives-prone
  $u_j\sim N(0,\sigma^2_{exam})$: some csets are systematically more inconclusives-prone
  $e_{ij} \sim N(0,\sigma^2)$: extra noise
  
```{r}
library(readxl)
library(dplyr)
library(stringr)
library(tidyr)
library(lme4)
library(tidyverse)

file_path <- "data/bullets_2024.xlsx"

kq_data <- read_excel(file_path, sheet = "KQ responses (n=1575)")
qq_data <- read_excel(file_path, sheet = "QQ responses (n=1581)")
cset_data <- read_excel(file_path, sheet = "Cset (n=1240)")
exam_data <- read_excel(file_path, sheet = "Summary by Participant (n=49)",skip = 1)

```

Data Cleaning

```{r}
phase_label <- "Primary (Baseline)"

kq <- kq_data %>%
  filter(Phase == phase_label) %>%
  mutate(
    Decision = if_else(K01_Q1value == "NoValue", "NoValue", K08_Conclusion),
    Comparison = "KQ"
  ) %>%
  select(AnonID, Cset, Mating, Decision, Comparison, K09_Difficulty) %>% rename(Difficulty = K09_Difficulty)

qq <- qq_data %>%
  filter(Phase == phase_label) %>%
  mutate(
    Decision = if_else(Q01_Q1value == "NoValue" | Q02_Q2value == "NoValue", "NoValue", Q08_Conclusion),
    Comparison = "QQ"
  ) %>%
  select(AnonID, Cset, Mating, Decision, Comparison, Q09_Difficulty) %>% rename(Difficulty = Q09_Difficulty)

cset <- cset_data %>%select( Cset, Type,`Cset Category (Detailed)`, `Cset Quality (voted)` ) %>%
  rename(Category = `Cset Category (Detailed)`, CsetQuality = `Cset Quality (voted)` )

responses <- bind_rows(kq, qq) %>%
  left_join(cset, by = "Cset") %>%
  mutate(Category = str_squish(Category), Decision = factor(Decision, levels = c("ID", "LeanID", "Insuff", "NoValue", "LeanExcl", "Excl")))
responses <- responses %>%
  separate(CsetQuality,
           into = c("Quality1", "Quality2"),
           sep = ":",
           remove = FALSE)

# Exclude Anon ID that doesn have accuracy calculated
exam_data %>% filter(Accuracy == 0) %>% pull("Participant (AnonID)") ->to_remove

exam_data %>% 
  filter(!`Participant (AnonID)` %in% to_remove) %>% 
  select(Accuracy,`Participant (AnonID)`) ->exam_data

responses_exam <- responses %>%
  filter(!`AnonID` %in% to_remove)

fit_responses <- left_join(responses_exam, exam_data, 
                       by = c("AnonID" = "Participant (AnonID)"))
responses <- responses %>%  mutate(
    Inconclusive = ifelse(Decision == "Insuff", 1, 0)
  )

responses <-responses %>%
  mutate(
    Error = case_when(
      Decision %in% c("Excl","LeanExcl") & Mating == "Mated" ~ 1,
      Decision %in% c("ID","LeanID") & Mating == "Nonmated" ~ 1,
      Decision == "Insuff" ~ NA_real_,
      TRUE ~ 0
    )
  ) %>%  mutate(
    Difficulty = na_if(Difficulty, "na")
  )

responses2 <- responses2 %>%
  mutate(Difficulty = fct_collapse(
    factor(Difficulty),
    "Easy"  = c("VEasy", "Easy"),  
    "Norm"  = "Norm",
    "Diff"  = "Diff",
    "VDiff" = "VDiff"
  ))
```


```{r}
fit_inc <- glmer(
  Inconclusive ~ Difficulty + Quality1 + Quality2 +  (1 | AnonID) + (1 | Cset), # + Mating + Comparison
  data = responses,
  family = binomial
)
summary(fit_inc)

fit_err <- glmer(
  Error ~ Difficulty + Quality1 + Quality2 + (1 | AnonID), # + (1 | Cset)
  data    = subset(responses2, Inconclusive == 0),
  family  = binomial,
  control = glmerControl(
    optimizer = "bobyqa",
    optCtrl   = list(maxfun = 2e5)
  )
)
summary(fit_err)
```

```{r}
# -----------------------------------------------------------------------------
# 0.  Helpers
inv_logit  <- function(x) 1 / (1 + exp(-x))
clamp_prob <- function(p, lo = 1e-6, hi = 1 - 1e-6) pmax(lo, pmin(hi, p))

# Factor level labels (used to label the simulated dataset)
DIFF_LEVELS  <- c("VEasy", "Easy", "Norm", "Diff", "VDiff")
QUAL1_LEVELS <- c("A", "B", "C")
QUAL2_LEVELS <- c("A", "B", "C", "D")


# -----------------------------------------------------------------------------
# 1.  one_simulation()
one_simulation <- function(

    per_diff        = rep(0.2, 5),
    per_exam_skill  = rep(1/3, 3),
    per_quality1    = c(1/3, 1/3, 1/3),
    per_quality2    = rep(0.25, 4),
    Hawthorne       = 0,
    n_examiners     = 30,
    nKQ             = 50,
    nQQ             = 50,
    mated_prop      = 0.5,
    seed            = NULL,

    beta_inc = list(
      # Intercept: log-odds of inconclusive at Diff / Q1=A / Q2=A, no Hawthorne
      intercept =  0.1495,

      # Difficulty offsets (order: VEasy, Easy, Norm, Diff[ref=0], VDiff)
      diff      = c(-17.2028, -5.0423, -1.1706, 0.0000, 0.9113),

      # Examiner skill offsets (Low[ref=0], Med, High)
      # Not estimated in fit_inc — set to 0 or override to add a skill effect
      skill     = c(0, 0, 0),

      # Quality1 offsets (A[ref=0], B, C)
      quality1  = c(0.0000, 0.5377, 1.6007),

      # Quality2 offsets (A[ref=0], B, C, D)
      quality2  = c(0.0000, 0.2857, 0.2219, 0.6841),

      # Hawthorne coefficient (alpha_H); multiplied by the Hawthorne argument
      hawthorne = 0.5
    ),
    sd_exam_inc = 1.1677,   # AnonID SD from fit_inc VarCorr
    sd_cset_inc = 0.8605,   # Cset   SD from fit_inc VarCorr

    # --- Error model: fitted from fit_err (bobyqa, responses2, no (1|Cset)) ---
    beta_err = list(
      # Intercept: log-odds of error at Diff / Q1=A / Q2=A
      intercept = -2.2259,

      # Difficulty offsets (order: VEasy, Easy, Norm, Diff[ref=0], VDiff)
      # VEasy collapsed into Easy during model fitting (zero errors in VEasy);
      # VEasy is assigned Easy's coefficient as the conservative default.
      diff      = c(-3.0829, -3.0829, -0.6228, 0.0000, 0.5032),
      #              VEasy    Easy     Norm     Diff    VDiff

      # Examiner skill offsets — not in fit_err, kept at 0
      # Override to add a skill effect: e.g. c(0.4, 0.0, -0.4) for Low/Med/High
      skill     = c(0, 0, 0),

      # Quality1 offsets (A[ref=0], B, C)
      quality1  = c(0.0000, 0.1779, 1.4058),

      # Quality2 offsets (A[ref=0], B, C, D)
      quality2  = c(0.0000, 0.6122, 0.5528, 0.7438),

      hawthorne = 0.0
    ),
    sd_exam_err = 0.9655,  # AnonID SD from fit_err VarCorr
    sd_cset_err = 0.0      # (1|Cset) not included in fit_err

) 
{

  if (!is.null(seed)) set.seed(seed)

  stopifnot(
    length(per_diff)       == 5,
    length(per_exam_skill) == 3,
    length(per_quality1)   == length(beta_inc$quality1),
    length(per_quality2)   == length(beta_inc$quality2),
    abs(sum(per_diff)       - 1) < 1e-8,
    abs(sum(per_exam_skill) - 1) < 1e-8,
    abs(sum(per_quality1)   - 1) < 1e-8,
    abs(sum(per_quality2)   - 1) < 1e-8
  )

  n_csets <- nKQ + nQQ

  # Step 1 — Simulate examiners
  examiners <- tibble(
    AnonID   = paste0("E", sprintf("%03d", seq_len(n_examiners))),
    SkillIdx = sample(1:3, n_examiners, replace = TRUE, prob = per_exam_skill),
    u_inc    = rnorm(n_examiners, 0, sd_exam_inc),
    u_err    = rnorm(n_examiners, 0, sd_exam_err)
  )


  # Step 2 — Simulate csets
  csets <- tibble(
    Cset       = paste0("C", sprintf("%04d", seq_len(n_csets))),
    Comparison = c(rep("KQ", nKQ), rep("QQ", nQQ)),
    Mating     = sample(c("Mated", "Nonmated"), n_csets, replace = TRUE,
                        prob = c(mated_prop, 1 - mated_prop)),
    DiffIdx    = sample(1:5, n_csets, replace = TRUE, prob = per_diff),
    Qual1Idx   = sample(seq_along(per_quality1), n_csets, replace = TRUE,
                        prob = per_quality1),
    Qual2Idx   = sample(seq_along(per_quality2), n_csets, replace = TRUE,
                        prob = per_quality2),
    Difficulty = DIFF_LEVELS[DiffIdx],
    Quality1   = QUAL1_LEVELS[Qual1Idx],
    Quality2   = QUAL2_LEVELS[Qual2Idx],
    v_inc      = rnorm(n_csets, 0, sd_cset_inc),
    v_err      = rnorm(n_csets, 0, sd_cset_err)
  )


  # Step 3 — Full crossed design  (every examiner sees every cset)

  sim_data <- tidyr::crossing(
    select(examiners, AnonID, SkillIdx, u_inc, u_err),
    select(csets, Cset, Comparison, Mating,
           DiffIdx, Qual1Idx, Qual2Idx,
           Difficulty, Quality1, Quality2,
           v_inc, v_err)
  )

  # Step 4 — Inconclusive outcome

  sim_data <- sim_data %>%
    mutate(
      lp_inc =
        beta_inc$intercept             +
        beta_inc$diff[DiffIdx]         +
        beta_inc$skill[SkillIdx]       +
        beta_inc$quality1[Qual1Idx]    +
        beta_inc$quality2[Qual2Idx]    +
        beta_inc$hawthorne * Hawthorne +
        u_inc + v_inc,

      p_inc        = clamp_prob(inv_logit(lp_inc)),
      Inconclusive = rbinom(n(), 1, p_inc)
    )


  # Step 5 — Error outcome  (conclusive rows only)

  # NOTE: dplyr::if_else() evaluates BOTH branches for all rows before
  # selecting, so passing p_err (NA for inconclusive rows) into rbinom()
  # produces NAs. We compute lp_err/p_err/Error only on conclusive rows
  # using a row index instead.
  sim_data <- sim_data %>%
    mutate(lp_err = NA_real_, p_err = NA_real_, Error = NA_integer_)

  conclusive_idx <- which(sim_data$Inconclusive == 0)

  sim_data$lp_err[conclusive_idx] <-
    beta_err$intercept +
    beta_err$diff[    sim_data$DiffIdx[ conclusive_idx]] +
    beta_err$skill[   sim_data$SkillIdx[conclusive_idx]] +
    beta_err$quality1[sim_data$Qual1Idx[conclusive_idx]] +
    beta_err$quality2[sim_data$Qual2Idx[conclusive_idx]] +
    beta_err$hawthorne * Hawthorne +
    sim_data$u_err[conclusive_idx] +
    sim_data$v_err[conclusive_idx]

  sim_data$p_err[conclusive_idx] <-
    clamp_prob(inv_logit(sim_data$lp_err[conclusive_idx]))

  sim_data$Error[conclusive_idx] <-
    rbinom(length(conclusive_idx), 1, sim_data$p_err[conclusive_idx])

  # Step 6 — Reconstruct Decision (mirrors real data coding)

  sim_data %>%
    mutate(
      Decision_D = case_when(
        Inconclusive == 1                        ~ "Insuff",
        Error == 0 & Mating == "Mated"           ~ "ID",
        Error == 0 & Mating == "Nonmated"        ~ "Excl",
        Error == 1 & Mating == "Mated"           ~ "Excl",    # false exclusion
        Error == 1 & Mating == "Nonmated"        ~ "ID",      # false ID
        TRUE                                     ~ NA_character_
      )
    )
}



# 2.  bootstrap_statistic()
#
#  Computes inc_rate and err_rate at three levels of aggregation:
#
#  OVERALL  : single rates across the whole dataset
#  BY ROW   : per Difficulty x Mating cell (row-level breakdown)
#  BY EXAMINER : one rate per examiner (AnonID)
#  BY CSET     : one rate per cset (Cset)
#
#  Returns a named list. The by_* elements are tibbles with one row per
#  group — these can be summarised across bootstrap replicates to get
#  group-specific CIs.

bootstrap_statistic <- function(df, decision_col = "Decision_D") {

  dec     <- df[[decision_col]]
  n_total <- nrow(df)
  n_inc   <- sum(dec == "Insuff",   na.rm = TRUE)
  n_conc  <- sum(dec != "Insuff" & !is.na(dec))
  conc_df <- df[!is.na(dec) & dec != "Insuff", ]
  n_err   <- sum(conc_df$Error == 1, na.rm = TRUE)


  # Overall rates

  overall <- list(
    inc_rate = n_inc / n_total,
    err_rate = if (n_conc > 0) n_err / n_conc else NA_real_,
    n_total  = n_total,
    n_inc    = n_inc,
    n_conc   = n_conc,
    n_err    = n_err
  )


  # By row  — breakdown by Difficulty x Mating cell
  # Each cell gets its own inc_rate and err_rate.

  by_row <- df %>%
    mutate(.dec = .data[[decision_col]]) %>%
    group_by(Difficulty, Mating) %>%
    summarise(
      n_total  = n(),
      n_inc    = sum(.dec == "Insuff",  na.rm = TRUE),
      n_conc   = sum(.dec != "Insuff" & !is.na(.dec)),
      n_err    = sum(Error == 1 & .dec != "Insuff", na.rm = TRUE),
      inc_rate = n_inc / n_total,
      err_rate = if_else(n_conc > 0, n_err / n_conc, NA_real_),
      .groups  = "drop"
    )


  # By examiner  — one inc_rate and err_rate per AnonID
  # Useful for detecting which examiners drive coverage failures.

  by_examiner <- df %>%
    mutate(.dec = .data[[decision_col]]) %>%
    group_by(AnonID) %>%
    summarise(
      n_total  = n(),
      n_inc    = sum(.dec == "Insuff",  na.rm = TRUE),
      n_conc   = sum(.dec != "Insuff" & !is.na(.dec)),
      n_err    = sum(Error == 1 & .dec != "Insuff", na.rm = TRUE),
      inc_rate = n_inc / n_total,
      err_rate = if_else(n_conc > 0, n_err / n_conc, NA_real_),
      .groups  = "drop"
    )


  # By cset  — one inc_rate and err_rate per Cset
  # Useful for detecting which csets are systematically hard.

  by_cset <- df %>%
    mutate(.dec = .data[[decision_col]]) %>%
    group_by(Cset, Difficulty, Mating) %>%
    summarise(
      n_total  = n(),
      n_inc    = sum(.dec == "Insuff",  na.rm = TRUE),
      n_conc   = sum(.dec != "Insuff" & !is.na(.dec)),
      n_err    = sum(Error == 1 & .dec != "Insuff", na.rm = TRUE),
      inc_rate = n_inc / n_total,
      err_rate = if_else(n_conc > 0, n_err / n_conc, NA_real_),
      .groups  = "drop"
    )

  list(
    overall      = overall,
    by_row       = by_row,
    by_examiner  = by_examiner,
    by_cset      = by_cset
  )
}






# 2.  true_parameters()
#  Computes the TRUE inc_rate and err_rate for a given scenario by averaging
#  over the fixed effects and random effect distributions analytically.
#  This is the "ground truth" the bootstrap CIs are evaluated against.
#  Because the logit link is nonlinear, E[inv_logit(lp)] != inv_logit(E[lp]).
#  We approximate via Monte Carlo integration over the random effects.

true_parameters <- function(
    per_diff       = rep(0.2, 5),
    per_exam_skill = rep(1/3, 3),
    per_quality1   = c(1/3, 1/3, 1/3),
    per_quality2   = rep(0.25, 4),
    Hawthorne      = 0,
    mated_prop     = 0.5,
    beta_inc = list(
      intercept =  0.1495,
      diff      = c(-17.2028, -5.0423, -1.1706, 0.0000, 0.9113),
      skill     = c(0, 0, 0),
      quality1  = c(0.0000, 0.5377, 1.6007),
      quality2  = c(0.0000, 0.2857, 0.2219, 0.6841),
      hawthorne = 0.5
    ),
    sd_exam_inc = 1.1677,
    sd_cset_inc = 0.8605,
    beta_err = list(
      intercept = -2.2259,
      diff      = c(-3.0829, -3.0829, -0.6228, 0.0000, 0.5032),
      skill     = c(0, 0, 0),
      quality1  = c(0.0000, 0.1779, 1.4058),
      quality2  = c(0.0000, 0.6122, 0.5528, 0.7438),
      hawthorne = 0.0
    ),
    sd_exam_err = 0.9655,
    sd_cset_err = 0.0,
    n_mc        = 50000
) {
  inv_logit <- plogis

  # draw covariate levels according to design proportions
  diff_id   <- sample(seq_along(per_diff),       n_mc, replace = TRUE, prob = per_diff)
  skill_id  <- sample(seq_along(per_exam_skill), n_mc, replace = TRUE, prob = per_exam_skill)
  q1_id     <- sample(seq_along(per_quality1),   n_mc, replace = TRUE, prob = per_quality1)
  q2_id     <- sample(seq_along(per_quality2),   n_mc, replace = TRUE, prob = per_quality2)

  # random effects
  u_inc <- rnorm(n_mc, 0, sd_exam_inc)
  v_inc <- rnorm(n_mc, 0, sd_cset_inc)
  u_err <- rnorm(n_mc, 0, sd_exam_err)
  v_err <- rnorm(n_mc, 0, sd_cset_err)

  # linear predictors for each MC draw
  eta_inc <- beta_inc$intercept +
    beta_inc$diff[diff_id] +
    beta_inc$skill[skill_id] +
    beta_inc$quality1[q1_id] +
    beta_inc$quality2[q2_id] +
    beta_inc$hawthorne * Hawthorne +
    u_inc + v_inc

  eta_err <- beta_err$intercept +
    beta_err$diff[diff_id] +
    beta_err$skill[skill_id] +
    beta_err$quality1[q1_id] +
    beta_err$quality2[q2_id] +
    beta_err$hawthorne * Hawthorne +
    u_err + v_err

  p_inc_mc <- inv_logit(eta_inc)
  p_err_mc <- inv_logit(eta_err)

  true_inc <- mean(p_inc_mc)
  true_err <- sum(p_err_mc * (1 - p_inc_mc)) / sum(1 - p_inc_mc)

  list(
    true_inc_rate = true_inc,
    true_err_rate = true_err,
    mated_prop    = mated_prop
  )
}


# 3.  simulate_coverage()

#  Single unified function replacing simulate_and_bootstrap() and
#  coverage_simulation(). All scenario arguments are specified once.

simulate_coverage <- function(

    M                = 200,
    B                = 500,
    bootstrap_method = c("row", "examiner", "cset"),
    conf_level       = 0.95,
    decision_col     = "Decision_D",
    seed             = 42,
    keep_last        = FALSE,
    return_data      = FALSE,
    ...
) {

  bootstrap_method <- match.arg(bootstrap_method)
  alpha  <- 1 - conf_level
  dots   <- list(...)   # scenario args — passed to both true_parameters() and one_simulation()

  # Step 1: compute true parameters for this scenario

  message("Computing true parameters via Monte Carlo integration...")
  true_par <- do.call(true_parameters, dots)
  message(sprintf(
    "  True inc_rate = %.4f  |  True err_rate = %.4f",
    true_par$true_inc_rate, true_par$true_err_rate
  ))


  # Step 2: outer loop — M repetitions

  message(sprintf(
    "Running %d repetitions x %d bootstrap replicates [method = '%s']...",
    M, B, bootstrap_method
  ))

  results   <- vector("list", M)
  last_boot <- NULL   # optionally stored for diagnostics

  for (m in seq_len(M)) {

    if (m %% 25 == 0) message(sprintf("  repetition %d / %d", m, M))

    set.seed(seed + m)   # deterministic per-repetition seed

    # --- 2a. Generate one synthetic dataset ----------------------------------
    sim_df   <- do.call(one_simulation, dots)
    obs_full <- bootstrap_statistic(sim_df, decision_col)
    obs_stat <- obs_full$overall   # scalar rates for coverage check

    # --- 2b. Bootstrap loop --------------------------------------------------
    boot_stats <- vector("list", B)

    for (b in seq_len(B)) {

      boot_df <- switch(bootstrap_method,

        "row" = {
          sim_df[sample(nrow(sim_df), nrow(sim_df), replace = TRUE), ]
        },

        "examiner" = {
          exams   <- unique(sim_df$AnonID)
          sampled <- sample(exams, length(exams), replace = TRUE)
          lapply(seq_along(sampled), function(i) {
            sim_df %>%
              filter(AnonID == sampled[i]) %>%
              mutate(AnonID = paste0(AnonID, "_b", i))
          }) %>% bind_rows()
        },

        "cset" = {
          cs      <- unique(sim_df$Cset)
          sampled <- sample(cs, length(cs), replace = TRUE)
          lapply(seq_along(sampled), function(i) {
            sim_df %>%
              filter(Cset == sampled[i]) %>%
              mutate(Cset = paste0(Cset, "_b", i))
          }) %>% bind_rows()
        }
      )

      s <- bootstrap_statistic(boot_df, decision_col)

      # Overall scalar stats — used for coverage CI
      boot_stats[[b]] <- tibble(
        inc_rate = s$overall$inc_rate,
        err_rate = s$overall$err_rate,
        n_total  = s$overall$n_total,
        n_inc    = s$overall$n_inc,
        n_conc   = s$overall$n_conc,
        n_err    = s$overall$n_err,

        # By-examiner mean rates (scalar summaries across examiners)
        inc_rate_exam_mean = mean(s$by_examiner$inc_rate, na.rm = TRUE),
        err_rate_exam_mean = mean(s$by_examiner$err_rate, na.rm = TRUE),
        inc_rate_exam_sd   = sd(s$by_examiner$inc_rate,   na.rm = TRUE),
        err_rate_exam_sd   = sd(s$by_examiner$err_rate,   na.rm = TRUE),

        # By-cset mean rates (scalar summaries across csets)
        inc_rate_cset_mean = mean(s$by_cset$inc_rate, na.rm = TRUE),
        err_rate_cset_mean = mean(s$by_cset$err_rate, na.rm = TRUE),
        inc_rate_cset_sd   = sd(s$by_cset$inc_rate,   na.rm = TRUE),
        err_rate_cset_sd   = sd(s$by_cset$err_rate,   na.rm = TRUE)
      )
    }

    boot_tbl <- bind_rows(boot_stats)

    # --- 2c. Percentile CI and coverage check (overall rates) ----------------
    ci_wide <- boot_tbl %>%
      summarise(
        inc_lo = quantile(inc_rate, alpha / 2,     na.rm = TRUE),
        inc_hi = quantile(inc_rate, 1 - alpha / 2, na.rm = TRUE),
        err_lo = quantile(err_rate, alpha / 2,     na.rm = TRUE),
        err_hi = quantile(err_rate, 1 - alpha / 2, na.rm = TRUE)
      )

    results[[m]] <- tibble(
      rep          = m,
      obs_inc_rate = obs_stat$inc_rate,
      obs_err_rate = obs_stat$err_rate,
      inc_lo       = ci_wide$inc_lo,
      inc_hi       = ci_wide$inc_hi,
      err_lo       = ci_wide$err_lo,
      err_hi       = ci_wide$err_hi,
      inc_covered  = (true_par$true_inc_rate >= ci_wide$inc_lo) &
                     (true_par$true_inc_rate <= ci_wide$inc_hi),
      err_covered  = (true_par$true_err_rate >= ci_wide$err_lo) &
                     (true_par$true_err_rate <= ci_wide$err_hi)
    )

    if (keep_last   && m == M) last_boot <- boot_tbl
    if (return_data && m == M) last_sim  <- sim_df
  }

  rep_tbl <- bind_rows(results)

  # Step 3: coverage summary

  coverage_summary <- tibble(
    statistic        = c("inc_rate", "err_rate"),
    true_value       = c(true_par$true_inc_rate, true_par$true_err_rate),
    coverage_rate    = c(mean(rep_tbl$inc_covered, na.rm = TRUE),
                         mean(rep_tbl$err_covered, na.rm = TRUE)),
    mean_ci_width    = c(mean(rep_tbl$inc_hi - rep_tbl$inc_lo, na.rm = TRUE),
                         mean(rep_tbl$err_hi - rep_tbl$err_lo, na.rm = TRUE)),
    nominal_coverage = conf_level,
    M                = M,
    B                = B,
    bootstrap_method = bootstrap_method
  )

  message("\n=== Coverage Summary ===")
  print(coverage_summary)

  out <- list(
    coverage_summary = coverage_summary,
    repetitions      = rep_tbl,
    true_parameters  = true_par,
    bootstrap_method = bootstrap_method,
    M                = M,
    B                = B,
    seed             = seed
  )
  if (keep_last)   out$last_boot_replicates <- last_boot
  if (return_data) out$simulated_data       <- last_sim
  out
}
```

```{r}
extract_var_prop <- function(fit) {
  vc <- as.data.frame(VarCorr(fit))
  vars <- setNames(vc$vcov, vc$grp)
  v_exam <- if ("AnonID" %in% names(vars)) vars["AnonID"] else 0
  v_cset <- if ("Cset"   %in% names(vars)) vars["Cset"]   else 0
  v_res  <- pi^2 / 3
  v_tot  <- v_exam + v_cset + v_res
  tibble(
    var_exam   = v_exam,
    var_cset   = v_cset,
    var_resid  = v_res,
    prop_exam  = v_exam / v_tot,
    prop_cset  = v_cset / v_tot,
    prop_resid = v_res / v_tot
  )
}

fit_models_once <- function(sim_df) {
  fit_inc <- tryCatch(
    glmer(
      Inconclusive ~ Difficulty + Quality1 + Quality2 + (1 | AnonID) + (1 | Cset),
      data = sim_df,
      family = binomial,
      control = glmerControl(
        optimizer = "bobyqa",
        optCtrl = list(maxfun = 2e5)
      )
    ),
    error = function(e) NULL
  )

  fit_err <- tryCatch(
    glmer(
      Error ~ Difficulty + Quality1 + Quality2 + (1 | AnonID),
      data = subset(sim_df, Inconclusive == 0),
      family = binomial,
      control = glmerControl(
        optimizer = "bobyqa",
        optCtrl = list(maxfun = 2e5)
      )
    ),
    error = function(e) NULL
  )

  inc_var <- if (!is.null(fit_inc)) {
    extract_var_prop(fit_inc)
  } else {
    tibble(
      var_exam = NA_real_, var_cset = NA_real_, var_resid = NA_real_,
      prop_exam = NA_real_, prop_cset = NA_real_, prop_resid = NA_real_
    )
  }

  err_var <- if (!is.null(fit_err)) {
    extract_var_prop(fit_err)
  } else {
    tibble(
      var_exam = NA_real_, var_cset = NA_real_, var_resid = NA_real_,
      prop_exam = NA_real_, prop_cset = NA_real_, prop_resid = NA_real_
    )
  }

  list(
    fit_inc = fit_inc,
    fit_err = fit_err,
    inc_var = inc_var,
    err_var = err_var
  )
}
```



```{r}
Sim_boot_cov <- function(
    per_diff        = rep(0.2, 5),
    per_exam_skill  = rep(1/3, 3),
    per_quality1    = c(1/3, 1/3, 1/3),
    per_quality2    = rep(0.25, 4),
    Hawthorne       = 0,
    n_examiners     = 30,
    nKQ             = 50,
    nQQ             = 50,
    mated_prop      = 0.5,

    beta_inc = list(
      intercept =  0.1495,
      diff      = c(-17.2028, -5.0423, -1.1706, 0.0000, 0.9113),
      skill     = c(0, 0, 0),
      quality1  = c(0.0000, 0.5377, 1.6007),
      quality2  = c(0.0000, 0.2857, 0.2219, 0.6841),
      hawthorne = 0.5
    ),
    sd_exam_inc = 1.1677,
    sd_cset_inc = 0.8605,

    beta_err = list(
      intercept = -2.2259,
      diff      = c(-3.0829, -3.0829, -0.6228, 0.0000, 0.5032),
      skill     = c(0, 0, 0),
      quality1  = c(0.0000, 0.1779, 1.4058),
      quality2  = c(0.0000, 0.6122, 0.5528, 0.7438),
      hawthorne = 0.0
    ),
    sd_exam_err = 0.9655,
    sd_cset_err = 0.0,

    M                = 200,
    B                = 500,
    bootstrap_method = c("row", "examiner", "cset"),
    conf_level       = 0.95,
    decision_col     = "Decision_D",
    seed             = 42,
    keep_last        = FALSE,
    return_data      = FALSE,
    fit_each_time    = TRUE,
    keep_last_fits   = FALSE
) {

  bootstrap_method <- match.arg(bootstrap_method)
  alpha <- 1 - conf_level

  true_par_args <- list(
    per_diff       = per_diff,
    per_exam_skill = per_exam_skill,
    per_quality1   = per_quality1,
    per_quality2   = per_quality2,
    Hawthorne      = Hawthorne,
    mated_prop     = mated_prop,
    beta_inc       = beta_inc,
    sd_exam_inc    = sd_exam_inc,
    sd_cset_inc    = sd_cset_inc,
    beta_err       = beta_err,
    sd_exam_err    = sd_exam_err,
    sd_cset_err    = sd_cset_err
  )

  sim_args <- c(true_par_args, list(
    n_examiners = n_examiners,
    nKQ         = nKQ,
    nQQ         = nQQ
  ))

  message("Computing true parameters via Monte Carlo integration...")
  true_par <- do.call(true_parameters, true_par_args)
  message(sprintf(
    "  True inc_rate = %.4f  |  True err_rate = %.4f",
    true_par$true_inc_rate, true_par$true_err_rate
  ))

  message(sprintf(
    "Running %d repetitions x %d bootstrap replicates [method = '%s']...",
    M, B, bootstrap_method
  ))

  results    <- vector("list", M)
  var_results <- vector("list", M)
  last_boot  <- NULL
  last_sim   <- NULL
  last_fits  <- NULL

  for (m in seq_len(M)) {

    if (m %% 25 == 0) message(sprintf("  repetition %d / %d", m, M))

    set.seed(seed + m)

    sim_df   <- do.call(one_simulation, sim_args)
    obs_stat <- bootstrap_statistic(sim_df, decision_col)$overall

    if (fit_each_time) {
      fits <- fit_models_once(sim_df)

      var_results[[m]] <- bind_cols(
        tibble(rep = m),
        rename_with(fits$inc_var, ~ paste0("inc_", .x)),
        rename_with(fits$err_var, ~ paste0("err_", .x))
      )

      if (keep_last_fits && m == M) last_fits <- fits
    }

    boot_stats <- vector("list", B)

    for (b in seq_len(B)) {

      boot_df <- switch(bootstrap_method,

        "row" = {
          sim_df[sample(nrow(sim_df), nrow(sim_df), replace = TRUE), ]
        },

        "examiner" = {
          exams   <- unique(sim_df$AnonID)
          sampled <- sample(exams, length(exams), replace = TRUE)
          lapply(seq_along(sampled), function(i) {
            sim_df %>%
              filter(AnonID == sampled[i]) %>%
              mutate(AnonID = paste0(AnonID, "_b", i))
          }) %>% bind_rows()
        },

        "cset" = {
          cs      <- unique(sim_df$Cset)
          sampled <- sample(cs, length(cs), replace = TRUE)
          lapply(seq_along(sampled), function(i) {
            sim_df %>%
              filter(Cset == sampled[i]) %>%
              mutate(Cset = paste0(Cset, "_b", i))
          }) %>% bind_rows()
        }
      )

      s <- bootstrap_statistic(boot_df, decision_col)$overall

      boot_stats[[b]] <- tibble(
        inc_rate = s$inc_rate,
        err_rate = s$err_rate,
        n_total  = s$n_total,
        n_inc    = s$n_inc,
        n_conc   = s$n_conc,
        n_err    = s$n_err
      )
    }

    boot_tbl <- bind_rows(boot_stats)

    ci_wide <- boot_tbl %>%
      summarise(
        inc_lo = quantile(inc_rate, alpha / 2,     na.rm = TRUE),
        inc_hi = quantile(inc_rate, 1 - alpha / 2, na.rm = TRUE),
        err_lo = quantile(err_rate, alpha / 2,     na.rm = TRUE),
        err_hi = quantile(err_rate, 1 - alpha / 2, na.rm = TRUE)
      )

    results[[m]] <- tibble(
      rep          = m,
      obs_inc_rate = obs_stat$inc_rate,
      obs_err_rate = obs_stat$err_rate,
      inc_lo       = ci_wide$inc_lo,
      inc_hi       = ci_wide$inc_hi,
      err_lo       = ci_wide$err_lo,
      err_hi       = ci_wide$err_hi,
      inc_covered  = (true_par$true_inc_rate >= ci_wide$inc_lo) &
                     (true_par$true_inc_rate <= ci_wide$inc_hi),
      err_covered  = (true_par$true_err_rate >= ci_wide$err_lo) &
                     (true_par$true_err_rate <= ci_wide$err_hi)
    )

    if (keep_last && m == M)   last_boot <- boot_tbl
    if (return_data && m == M) last_sim  <- sim_df
  }

  rep_tbl <- bind_rows(results)

  coverage_summary <- tibble(
    statistic        = c("inc_rate", "err_rate"),
    true_value       = c(true_par$true_inc_rate, true_par$true_err_rate),
    coverage_rate    = c(mean(rep_tbl$inc_covered, na.rm = TRUE),
                         mean(rep_tbl$err_covered, na.rm = TRUE)),
    mean_ci_width    = c(mean(rep_tbl$inc_hi - rep_tbl$inc_lo, na.rm = TRUE),
                         mean(rep_tbl$err_hi - rep_tbl$err_lo, na.rm = TRUE)),
    nominal_coverage = conf_level,
    M                = M,
    B                = B,
    bootstrap_method = bootstrap_method
  )

  variance_summary <- NULL
  variance_repetitions <- NULL

  if (fit_each_time) {
    variance_repetitions <- bind_rows(var_results)

    variance_summary <- tibble(
      model = c("Inconclusive", "Error"),
      mean_exam_share = c(
        mean(variance_repetitions$inc_prop_exam, na.rm = TRUE),
        mean(variance_repetitions$err_prop_exam, na.rm = TRUE)
      ),
      mean_cset_share = c(
        mean(variance_repetitions$inc_prop_cset, na.rm = TRUE),
        mean(variance_repetitions$err_prop_cset, na.rm = TRUE)
      ),
      mean_resid_share = c(
        mean(variance_repetitions$inc_prop_resid, na.rm = TRUE),
        mean(variance_repetitions$err_prop_resid, na.rm = TRUE)
      ),
      mean_exam_var = c(
        mean(variance_repetitions$inc_var_exam, na.rm = TRUE),
        mean(variance_repetitions$err_var_exam, na.rm = TRUE)
      ),
      mean_cset_var = c(
        mean(variance_repetitions$inc_var_cset, na.rm = TRUE),
        mean(variance_repetitions$err_var_cset, na.rm = TRUE)
      )
    )
  }

  message("\n=== Coverage Summary ===")
  print(coverage_summary)

  if (fit_each_time) {
    message("\n=== Variance Share Summary ===")
    print(variance_summary)
  }

  out <- list(
    coverage_summary     = coverage_summary,
    repetitions          = rep_tbl,
    true_parameters      = true_par,
    bootstrap_method     = bootstrap_method,
    M                    = M,
    B                    = B,
    seed                 = seed,
    variance_summary     = variance_summary,
    variance_repetitions = variance_repetitions
  )

  if (keep_last)      out$last_boot_replicates <- last_boot
  if (return_data)    out$simulated_data       <- last_sim
  if (keep_last_fits) out$last_fits            <- last_fits

  out
}
```

```{r}
 Sim_boot_cov(
  M           = 100,          # one dataset
  B           = 100,       # 2000 bootstrap draws
  keep_last   = TRUE,       # keep the bootstrap replicates tibble
  return_data = TRUE,       # keep the simulated dataset
  bootstrap_method = "examiner",
  seed             = 42,
  per_diff         = rep(0.2, 5),
  per_quality1    = c(1/3, 1/3, 1/3),
  per_quality2    = rep(0.25, 4),
 Hawthorne    = 0,
  n_examiners      = 49,
  nKQ              = 50,
  nQQ              = 50
)


 Sim_boot_cov(
  M           = 100,          # one dataset
  B           = 100,       # 2000 bootstrap draws
  keep_last   = TRUE,       # keep the bootstrap replicates tibble
  return_data = TRUE,       # keep the simulated dataset
  bootstrap_method = "examiner",
  seed             = 42,
  per_diff         = c(0.3,0.3,0.2,0.1,0.1),
  per_quality1    = c(1/3, 1/3, 1/3),
  per_quality2    = rep(0.25, 4),
 Hawthorne    = 0,
  n_examiners      = 49,
  nKQ              = 50,
  nQQ              = 50
)
```


