---
title: "Simulation Study: Bootstrap Coverage for Forensic Examiner Error Rates"
output:
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```


# Libraries

```{r libraries}
library(readxl)
library(dplyr)
library(stringr)
library(tidyr)
library(forcats)
library(lme4)
library(ggplot2)
library(scales)
library(purrr)
```


#  Load and Clean Real Data

# Using real data here just to fit the model pieces.
# After this, everything runs on simulated data.

```{r }
file_path <- "data/bullets_2024.xlsx" 

kq_data   <- read_excel(file_path, sheet = "KQ responses (n=1575)")
qq_data   <- read_excel(file_path, sheet = "QQ responses (n=1581)")
cset_data <- read_excel(file_path, sheet = "Cset (n=1240)")
```

```{r }
phase_label <- "Primary (Baseline)"

# Building the KQ table here.
# If Q1 is NoValue, the whole response stays NoValue.
kq <- kq_data %>%
  filter(Phase == phase_label) %>%
  mutate(
    Decision   = if_else(K01_Q1value == "NoValue", "NoValue", K08_Conclusion),
    Comparison = "KQ"
  ) %>%
  select(AnonID, Cset, Mating, Decision, Comparison, K09_Difficulty) %>%
  rename(Difficulty = K09_Difficulty)

# Building the QQ table here.
# Same idea, but either Q1 or Q2 can trigger NoValue.
qq <- qq_data %>%
  filter(Phase == phase_label) %>%
  mutate(
    Decision   = if_else(
      Q01_Q1value == "NoValue" | Q02_Q2value == "NoValue",
      "NoValue", Q08_Conclusion
    ),
    Comparison = "QQ"
  ) %>%
  select(AnonID, Cset, Mating, Decision, Comparison, Q09_Difficulty) %>%
  rename(Difficulty = Q09_Difficulty)

# Pulling cset info here.
cset <- cset_data %>%
  select(Cset, Type, `Cset Category (Detailed)`, `Cset Quality (voted)`) %>%
  rename(Category    = `Cset Category (Detailed)`,
         CsetQuality = `Cset Quality (voted)`)

# Joining everything and making outcome columns here.
responses <- bind_rows(kq, qq) %>%
  left_join(cset, by = "Cset") %>%
  mutate(
    Category = str_squish(Category),
    Decision = factor(Decision,
                      levels = c("ID","LeanID","Insuff","NoValue","LeanExcl","Excl"))
  ) %>%
  # Splitting quality into two separate model columns.

  separate(CsetQuality, into = c("Quality1", "Quality2"), sep = ":", remove = FALSE) %>%
  mutate(
    # Marking Insuff as inconclusive here.
    # NoValue is a data issue, so leaving it out.

    Inconclusive = as.integer(Decision == "Insuff"),

    # Marking wrong conclusive calls as errors here.
    # Inconclusive rows stay NA and skip the error model.

    Error = case_when(
      Decision %in% c("Excl","LeanExcl") & Mating == "Mated"    ~ 1,
      Decision %in% c("ID","LeanID")     & Mating == "Nonmated" ~ 1,
      Decision %in% c("Insuff","NoValue")                        ~ NA_real_,
      TRUE                                                        ~ 0
    ),

    Difficulty = na_if(Difficulty, "na")   # "na" strings → proper NA
  )

# Collapsing VEasy into Easy here for the error model.
# Doing this keeps the fit from blowing up.

responses2 <- responses %>%
  mutate(Difficulty = fct_collapse(
    factor(Difficulty),
    "Easy"  = c("VEasy", "Easy"),
    "Norm"  = "Norm",
    "Diff"  = "Diff",
    "VDiff" = "VDiff"
  ))
```


# Fitting Real-Data Models

# Fitting these once to get the simulation parameters.
# Later runs use these values instead of refitting every time.

```{r }
# Fitting the inconclusive model here.
# This picks up both examiner and item-level variation.

fit_inc <- glmer(
  Inconclusive ~ Difficulty + Quality1 + Quality2 + (1 | AnonID) + (1 | Cset),
  data    = responses,
  family  = binomial
)
summary(fit_inc)

# Fitting the error model here.
# Keeping only examiner effects makes this one behave better.

fit_err <- glmer(
  Error ~ Difficulty + Quality1 + Quality2 + (1 | AnonID),
  data    = subset(responses2, Inconclusive == 0),
  family  = binomial,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)
summary(fit_err)

```


# Simulation Functions

## Helpers

```{r }
# Turning log-odds into probabilities here.

inv_logit  <- function(x) 1 / (1 + exp(-x))

# Nudging probs away from exact 0 and 1 here.
# Doing this keeps rbinom() safe.

clamp_prob <- function(p, lo = 1e-6, hi = 1 - 1e-6) pmax(lo, pmin(hi, p))

# Using lookup labels here for the integer-coded values.
# It stays faster this way.

DIFF_LEVELS  <- c("VEasy", "Easy", "Norm", "Diff", "VDiff")
QUAL1_LEVELS <- c("A", "B", "C")
QUAL2_LEVELS <- c("A", "B", "C", "D")
```

## b. one_simulation() - this generate one complete fake simulation study

# Building one full fake study here.
# Inputs control difficulty, skill mix, and Hawthorne effects.

```{r }
one_simulation <- function(

  # Setting the scenario inputs here.
  per_diff        = rep(0.2, 5),       # [VEasy, Easy, Norm, Diff, VDiff] proportions
  per_exam_skill  = rep(1/3, 3),       # [Low, Medium, High] examiner skill proportions
  per_quality1    = c(1/3, 1/3, 1/3), # Q1 quality [A, B, C] proportions
  per_quality2    = rep(0.25, 4),      # Q2 quality [A, B, C, D] proportions
  Hawthorne       = 0,                 # 0 = no effect; 1 = full Hawthorne shift
  n_examiners     = 49,
  nKQ             = 50,
  nQQ             = 50,
  mated_prop      = 0.5,
  seed            = NULL,

  # Plugging in inconclusive-model parameters here.
  # These come from the fitted real-data model.


  beta_inc = list(
    intercept =  0.1495,
    diff      = c(-17.2028, -5.0423, -1.1706, 0.0000, 0.9113),
    skill     = c(0, 0, 0),
    quality1  = c(0.0000, 0.5377, 1.6007),
    quality2  = c(0.0000, 0.2857, 0.2219, 0.6841),
    hawthorne = 0.5
  ),
  sd_exam_inc = 1.1677,   # between-examiner SD from fit_inc VarCorr
  sd_cset_inc = 0.8605,   # between-cset SD from fit_inc VarCorr

  # Plugging in error-model parameters here.
  # Hawthorne only shifts inconclusive calls, not errors.

  beta_err = list(
    intercept = -2.2259,
    diff      = c(-3.0829, -3.0829, -0.6228, 0.0000, 0.5032),
    skill     = c(0, 0, 0),
    quality1  = c(0.0000, 0.1779, 1.4058),
    quality2  = c(0.0000, 0.6122, 0.5528, 0.7438),
    hawthorne = 0.0
  ),
  sd_exam_err = 0.9655,   # between-examiner SD from fit_err VarCorr
  sd_cset_err = 0.0       # not in fit_err (item RE was dropped)

) {
  if (!is.null(seed)) set.seed(seed)

  # Checking the proportions sum to 1 here.
  stopifnot(
    length(per_diff) == 5, length(per_exam_skill) == 3,
    length(per_quality1) == length(beta_inc$quality1),
    length(per_quality2) == length(beta_inc$quality2),
    abs(sum(per_diff) - 1) < 1e-8, abs(sum(per_exam_skill) - 1) < 1e-8,
    abs(sum(per_quality1) - 1) < 1e-8, abs(sum(per_quality2) - 1) < 1e-8
  )

  n_csets <- nKQ + nQQ

  # Drawing examiner effects here.
  # Each examiner keeps the same tendency across all items.

  examiners <- tibble(
    AnonID   = paste0("E", sprintf("%03d", seq_len(n_examiners))),
    SkillIdx = sample(1:3, n_examiners, replace = TRUE, prob = per_exam_skill),
    u_inc    = rnorm(n_examiners, 0, sd_exam_inc),
    u_err    = rnorm(n_examiners, 0, sd_exam_err)
  )

  # Drawing cset effects and assigning features here.
  # This is where the difficulty mix gets set.

  csets <- tibble(
    Cset       = paste0("C", sprintf("%04d", seq_len(n_csets))),
    Comparison = c(rep("KQ", nKQ), rep("QQ", nQQ)),
    Mating     = sample(c("Mated","Nonmated"), n_csets, replace = TRUE,
                        prob = c(mated_prop, 1 - mated_prop)),
    DiffIdx    = sample(1:5, n_csets, replace = TRUE, prob = per_diff),
    Qual1Idx   = sample(seq_along(per_quality1), n_csets, replace = TRUE,
                        prob = per_quality1),
    Qual2Idx   = sample(seq_along(per_quality2), n_csets, replace = TRUE,
                        prob = per_quality2),
    Difficulty = DIFF_LEVELS[DiffIdx],
    Quality1   = QUAL1_LEVELS[Qual1Idx],
    Quality2   = QUAL2_LEVELS[Qual2Idx],
    v_inc      = rnorm(n_csets, 0, sd_cset_inc),
    v_err      = rnorm(n_csets, 0, sd_cset_err)
  )

  # Crossing every examiner with every cset here.
  # This matches the original study setup.

  sim_data <- tidyr::crossing(
    select(examiners, AnonID, SkillIdx, u_inc, u_err),
    select(csets, Cset, Comparison, Mating, DiffIdx, Qual1Idx, Qual2Idx,
           Difficulty, Quality1, Quality2, v_inc, v_err)
  )

  # Generating inconclusive calls here.
  # Build the probability, then sample the outcome.

  sim_data <- sim_data %>%
    mutate(
      lp_inc =
        beta_inc$intercept          +
        beta_inc$diff[DiffIdx]      +
        beta_inc$skill[SkillIdx]    +
        beta_inc$quality1[Qual1Idx] +
        beta_inc$quality2[Qual2Idx] +
        beta_inc$hawthorne * Hawthorne +
        u_inc + v_inc,
      p_inc        = clamp_prob(inv_logit(lp_inc)),
      Inconclusive = rbinom(n(), 1, p_inc)
    )

  # Generating errors only for conclusive rows here.
  # Using indexing so the NA rows do not break things.

  sim_data <- sim_data %>%
    mutate(lp_err = NA_real_, p_err = NA_real_, Error = NA_integer_)

  conclusive_idx <- which(sim_data$Inconclusive == 0)

  sim_data$lp_err[conclusive_idx] <-
    beta_err$intercept +
    beta_err$diff[    sim_data$DiffIdx[ conclusive_idx]] +
    beta_err$skill[   sim_data$SkillIdx[conclusive_idx]] +
    beta_err$quality1[sim_data$Qual1Idx[conclusive_idx]] +
    beta_err$quality2[sim_data$Qual2Idx[conclusive_idx]] +
    beta_err$hawthorne * Hawthorne +
    sim_data$u_err[conclusive_idx] +
    sim_data$v_err[conclusive_idx]

  sim_data$p_err[conclusive_idx] <-
    clamp_prob(inv_logit(sim_data$lp_err[conclusive_idx]))

  sim_data$Error[conclusive_idx] <-
    rbinom(length(conclusive_idx), 1, sim_data$p_err[conclusive_idx])

  # Rebuilding decision labels here.
  # This keeps the coding aligned with the real data.

  sim_data %>%
    mutate(
      Decision_D = case_when(
        Inconclusive == 1                 ~ "Insuff",
        Error == 0 & Mating == "Mated"    ~ "ID",      # correct identification
        Error == 0 & Mating == "Nonmated" ~ "Excl",    # correct exclusion
        Error == 1 & Mating == "Mated"    ~ "Excl",    # false exclusion (FN)
        Error == 1 & Mating == "Nonmated" ~ "ID",      # false ID (FP)
        TRUE                              ~ NA_character_
      )
    )
}
```

## bootstrap_statistic() — summarise one dataset

# Summarizing the dataset here.
# Getting overall, by-examiner, and by-cset rates.

```{r }
bootstrap_statistic <- function(df, decision_col = "Decision_D") {

  dec    <- df[[decision_col]]
  n_tot  <- nrow(df)
  n_inc  <- sum(dec == "Insuff", na.rm = TRUE)
  n_conc <- sum(dec != "Insuff" & !is.na(dec))
  conc   <- df[!is.na(dec) & dec != "Insuff", ]
  n_err  <- sum(conc$Error == 1, na.rm = TRUE)

  # Getting the overall rates here.
  overall <- list(
    inc_rate = n_inc / n_tot,
    err_rate = if (n_conc > 0) n_err / n_conc else NA_real_,
    n_total  = n_tot, n_inc = n_inc, n_conc = n_conc, n_err = n_err
  )

  # Breaking results out by examiner here.
  by_examiner <- df %>%
    mutate(.dec = .data[[decision_col]]) %>%
    group_by(AnonID) %>%
    summarise(
      n_total  = n(),
      n_inc    = sum(.dec == "Insuff", na.rm = TRUE),
      n_conc   = sum(.dec != "Insuff" & !is.na(.dec)),
      n_err    = sum(Error == 1 & .dec != "Insuff", na.rm = TRUE),
      inc_rate = n_inc / n_total,
      err_rate = if_else(n_conc > 0, n_err / n_conc, NA_real_),
      .groups  = "drop"
    )

  # Breaking results out by cset here.
  by_cset <- df %>%
    mutate(.dec = .data[[decision_col]]) %>%
    group_by(Cset, Difficulty, Mating) %>%
    summarise(
      n_total  = n(),
      n_inc    = sum(.dec == "Insuff",  na.rm = TRUE),
      n_conc   = sum(.dec != "Insuff" & !is.na(.dec)),
      n_err    = sum(Error == 1 & .dec != "Insuff", na.rm = TRUE),
      inc_rate = n_inc / n_total,
      err_rate = if_else(n_conc > 0, n_err / n_conc, NA_real_),
      .groups  = "drop"
    )

  list(overall = overall, by_examiner = by_examiner, by_cset = by_cset)
}
```

## true_parameters() — ground truth via Monte Carlo integration

# Estimating the true rates here with Monte Carlo draws.
# Sampling many combinations gives the marginal truth for the scenario.

```{r }

true_parameters <- function(
    per_diff       = rep(0.2, 5),
    per_exam_skill = rep(1/3, 3),
    per_quality1   = c(1/3, 1/3, 1/3),
    per_quality2   = rep(0.25, 4),
    Hawthorne      = 0,
    mated_prop     = 0.5,
    beta_inc = list(
      intercept =  0.1495,
      diff      = c(-17.2028, -5.0423, -1.1706, 0.0000, 0.9113),
      skill     = c(0, 0, 0),
      quality1  = c(0.0000, 0.5377, 1.6007),
      quality2  = c(0.0000, 0.2857, 0.2219, 0.6841),
      hawthorne = 0.5
    ),
    sd_exam_inc = 1.1677,
    sd_cset_inc = 0.8605,
    beta_err = list(
      intercept = -2.2259,
      diff      = c(-3.0829, -3.0829, -0.6228, 0.0000, 0.5032),
      skill     = c(0, 0, 0),
      quality1  = c(0.0000, 0.1779, 1.4058),
      quality2  = c(0.0000, 0.6122, 0.5528, 0.7438),
      hawthorne = 0.0
    ),
    sd_exam_err = 0.9655,
    sd_cset_err = 0.0,
    n_mc        = 50000     # more draws = more accurate, but slower
) {

  # Sampling covariates fresh on every draw here.
  # Doing this avoids the old averaging shortcut.

  diff_id  <- sample(seq_along(per_diff),       n_mc, replace = TRUE, prob = per_diff)
  skill_id <- sample(seq_along(per_exam_skill), n_mc, replace = TRUE, prob = per_exam_skill)
  q1_id    <- sample(seq_along(per_quality1),   n_mc, replace = TRUE, prob = per_quality1)
  q2_id    <- sample(seq_along(per_quality2),   n_mc, replace = TRUE, prob = per_quality2)

  # Drawing random effects separately here.
  u_inc <- rnorm(n_mc, 0, sd_exam_inc)
  v_inc <- rnorm(n_mc, 0, sd_cset_inc)
  u_err <- rnorm(n_mc, 0, sd_exam_err)
  v_err <- rnorm(n_mc, 0, sd_cset_err)

  # Building the full linear predictors here.
  eta_inc <- beta_inc$intercept + beta_inc$diff[diff_id]  +
             beta_inc$skill[skill_id] + beta_inc$quality1[q1_id] +
             beta_inc$quality2[q2_id] + beta_inc$hawthorne * Hawthorne +
             u_inc + v_inc

  eta_err <- beta_err$intercept + beta_err$diff[diff_id]  +
             beta_err$skill[skill_id] + beta_err$quality1[q1_id] +
             beta_err$quality2[q2_id] + beta_err$hawthorne * Hawthorne +
             u_err + v_err

  p_inc <- inv_logit(eta_inc)
  p_err <- inv_logit(eta_err)

  # Computing the true error rate conditional on being conclusive.
  # Only non-inconclusive responses can contribute errors.

  list(
    true_inc_rate = mean(p_inc),
    true_err_rate = sum(p_err * (1 - p_inc)) / sum(1 - p_inc),
    mated_prop    = mated_prop
  )
}
```

##  extract_var_prop() and fit_models_once() — variance validation helpers

# Using these as diagnostics after simulation.
# Refit the models and see if the variance pieces come back close.

```{r }
# Pulling variance shares out of a fitted model here.
extract_var_prop <- function(fit) {
  vc     <- as.data.frame(VarCorr(fit))
  vars   <- setNames(vc$vcov, vc$grp)
  v_exam <- if ("AnonID" %in% names(vars)) vars["AnonID"] else 0
  v_cset <- if ("Cset"   %in% names(vars)) vars["Cset"]   else 0
  v_res  <- pi^2 / 3
  v_tot  <- v_exam + v_cset + v_res
  tibble(var_exam  = v_exam,  var_cset   = v_cset,  var_resid = v_res,
         prop_exam = v_exam / v_tot, prop_cset = v_cset / v_tot,
         prop_resid = v_res / v_tot)
}

# Refitting both models on one simulated dataset .

fit_models_once <- function(sim_df) {

  fit_inc_sim <- tryCatch(
    glmer(Inconclusive ~ Difficulty + Quality1 + Quality2 + (1|AnonID) + (1|Cset),
          data = sim_df, family = binomial,
          control = glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))),
    error = function(e) NULL
  )

  sim_err_df <- sim_df %>%
    filter(Inconclusive == 0) %>%
    mutate(Difficulty = as.character(Difficulty),
           Difficulty = if_else(Difficulty == "VEasy", "Easy", Difficulty),
           Difficulty = factor(Difficulty, levels = c("Easy","Norm","Diff","VDiff")))

  fit_err_sim <- tryCatch(
    glmer(Error ~ Difficulty + Quality1 + Quality2 + (1|AnonID),
          data = sim_err_df, family = binomial,
          control = glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))),
    error = function(e) NULL
  )

  na_row <- tibble(var_exam=NA_real_, var_cset=NA_real_, var_resid=NA_real_,
                   prop_exam=NA_real_, prop_cset=NA_real_, prop_resid=NA_real_)

  list(fit_inc = fit_inc_sim, fit_err = fit_err_sim,
       inc_var = if (!is.null(fit_inc_sim)) extract_var_prop(fit_inc_sim) else na_row,
       err_var = if (!is.null(fit_err_sim)) extract_var_prop(fit_err_sim) else na_row)
}
```

##  Sim_boot_cov() - the main coverage simulation function

# Running one full coverage simulation here.
# This ties together truth, simulation, bootstrap, and CI checks.

```{r }
Sim_boot_cov <- function(
    per_diff        = rep(0.2, 5),
    per_exam_skill  = rep(1/3, 3),
    per_quality1    = c(1/3, 1/3, 1/3),
    per_quality2    = rep(0.25, 4),
    Hawthorne       = 0,
    n_examiners     = 49,
    nKQ             = 50,
    nQQ             = 50,
    mated_prop      = 0.5,
    beta_inc = list(intercept=0.1495,
                    diff=c(-17.2028,-5.0423,-1.1706,0.0000,0.9113),
                    skill=c(0,0,0), quality1=c(0.0000,0.5377,1.6007),
                    quality2=c(0.0000,0.2857,0.2219,0.6841), hawthorne=0.5),
    sd_exam_inc = 1.1677, sd_cset_inc = 0.8605,
    beta_err = list(intercept=-2.2259,
                    diff=c(-3.0829,-3.0829,-0.6228,0.0000,0.5032),
                    skill=c(0,0,0), quality1=c(0.0000,0.1779,1.4058),
                    quality2=c(0.0000,0.6122,0.5528,0.7438), hawthorne=0.0),
    sd_exam_err = 0.9655, sd_cset_err = 0.0,
    M                = 200,   # outer repetitions (datasets generated)
    B                = 500,   # bootstrap draws per repetition
    bootstrap_method = c("row", "examiner", "cset"),
    conf_level       = 0.95,
    decision_col     = "Decision_D",
    seed             = 42,
    keep_last        = FALSE,  # if TRUE: return last repetition's bootstrap table
    return_data      = FALSE,  # if TRUE: return last repetition's simulated dataset
    fit_each_time    = FALSE   # if TRUE: refit models for variance validation (slow)
) {
  bootstrap_method <- match.arg(bootstrap_method)
  alpha <- 1 - conf_level

  # Keeping args separate here because true_parameters() takes fewer inputs.
  true_par_args <- list(per_diff=per_diff, per_exam_skill=per_exam_skill,
                        per_quality1=per_quality1, per_quality2=per_quality2,
                        Hawthorne=Hawthorne, mated_prop=mated_prop,
                        beta_inc=beta_inc, sd_exam_inc=sd_exam_inc,
                        sd_cset_inc=sd_cset_inc, beta_err=beta_err,
                        sd_exam_err=sd_exam_err, sd_cset_err=sd_cset_err)

  sim_args <- c(true_par_args,
                list(n_examiners=n_examiners, nKQ=nKQ, nQQ=nQQ))

  # Getting the ground-truth rates here.
  message("Computing true parameters via Monte Carlo...")
  true_par <- do.call(true_parameters, true_par_args)
  message(sprintf("  true_inc_rate = %.4f  |  true_err_rate = %.4f",
                  true_par$true_inc_rate, true_par$true_err_rate))
  message(sprintf("Running %d reps × %d boots [method = %s]...",
                  M, B, bootstrap_method))

  results   <- vector("list", M)
  var_rows  <- if (fit_each_time) vector("list", M) else NULL
  last_boot <- NULL; last_sim <- NULL

  for (m in seq_len(M)) {
    if (m %% 25 == 0) message(sprintf("  rep %d / %d", m, M))
    set.seed(seed + m)

    # Generating one fake dataset here.
    sim_df   <- do.call(one_simulation, sim_args)
    obs_stat <- bootstrap_statistic(sim_df, decision_col)$overall

    # Optionally refitting models here for variance checks.
    if (fit_each_time) {
      fits <- fit_models_once(sim_df)
      var_rows[[m]] <- bind_cols(
        tibble(rep = m),
        rename_with(fits$inc_var, ~paste0("inc_", .x)),
        rename_with(fits$err_var, ~paste0("err_", .x))
      )
    }

    # Running the bootstrap loop .
    boot_stats <- vector("list", B)
    for (b in seq_len(B)) {
      boot_df <- switch(bootstrap_method,

        # Resampling rows here.
        # This ignores both clustering levels.
        "row" = sim_df[sample(nrow(sim_df), nrow(sim_df), replace = TRUE), ],

        # Resampling whole examiners here.
        # Renaming duplicates keeps them from getting merged.
        "examiner" = {
          exams   <- unique(sim_df$AnonID)
          sampled <- sample(exams, length(exams), replace = TRUE)
          lapply(seq_along(sampled), function(i)
            sim_df %>% filter(AnonID == sampled[i]) %>%
              mutate(AnonID = paste0(AnonID, "_b", i))) %>% bind_rows()
        },

        # Resampling whole csets here.
        # Renaming duplicates keeps them separate.
        "cset" = {
          cs      <- unique(sim_df$Cset)
          sampled <- sample(cs, length(cs), replace = TRUE)
          lapply(seq_along(sampled), function(i)
            sim_df %>% filter(Cset == sampled[i]) %>%
              mutate(Cset = paste0(Cset, "_b", i))) %>% bind_rows()
        }
      )

      s <- bootstrap_statistic(boot_df, decision_col)$overall
      boot_stats[[b]] <- tibble(inc_rate = s$inc_rate, err_rate = s$err_rate)
    }

    boot_tbl <- bind_rows(boot_stats)

    # Building percentile CIs here.
    ci <- boot_tbl %>%
      summarise(
        inc_lo = quantile(inc_rate, alpha / 2,     na.rm = TRUE),
        inc_hi = quantile(inc_rate, 1 - alpha / 2, na.rm = TRUE),
        err_lo = quantile(err_rate, alpha / 2,     na.rm = TRUE),
        err_hi = quantile(err_rate, 1 - alpha / 2, na.rm = TRUE)
      )

    # Checking whether the CI covers the true value here.
    results[[m]] <- tibble(
      rep = m,
      obs_inc_rate = obs_stat$inc_rate, obs_err_rate = obs_stat$err_rate,
      inc_lo = ci$inc_lo, inc_hi = ci$inc_hi,
      err_lo = ci$err_lo, err_hi = ci$err_hi,
      inc_covered = (true_par$true_inc_rate >= ci$inc_lo &
                     true_par$true_inc_rate <= ci$inc_hi),
      err_covered = (true_par$true_err_rate >= ci$err_lo &
                     true_par$true_err_rate <= ci$err_hi)
    )

    if (keep_last   && m == M) last_boot <- boot_tbl
    if (return_data && m == M) last_sim  <- sim_df
  }

  rep_tbl <- bind_rows(results)

  # Summarizing coverage across all reps here.
  coverage_summary <- tibble(
    statistic        = c("inc_rate", "err_rate"),
    true_value       = c(true_par$true_inc_rate, true_par$true_err_rate),
    coverage_rate    = c(mean(rep_tbl$inc_covered, na.rm = TRUE),
                         mean(rep_tbl$err_covered, na.rm = TRUE)),
    mean_ci_width    = c(mean(rep_tbl$inc_hi - rep_tbl$inc_lo, na.rm = TRUE),
                         mean(rep_tbl$err_hi - rep_tbl$err_lo, na.rm = TRUE)),
    nominal_coverage = conf_level, M = M, B = B,
    bootstrap_method = bootstrap_method
  )

  message("\n Coverage Summary"); print(coverage_summary)

  out <- list(coverage_summary = coverage_summary, repetitions = rep_tbl,
              true_parameters = true_par, bootstrap_method = bootstrap_method,
              M = M, B = B, seed = seed)
  if (keep_last)   out$last_boot_replicates <- last_boot
  if (return_data) out$simulated_data       <- last_sim
  if (fit_each_time) out$variance_repetitions <- bind_rows(var_rows)
  out
}
```

##  compare_coverage_scenarios() —  wrapper for multi-scenario runs

# Running a bunch of named scenarios here.
# This makes side-by-side comparisons easier.

```{r }
compare_coverage_scenarios <- function(scenarios, ...) {
  # Each scenario overrides shared settings here.

  shared_args <- list(...)

  all_results <- lapply(names(scenarios), function(nm) {
    message(sprintf("\n Scenario: %s ", nm))
    args <- modifyList(shared_args, scenarios[[nm]])
    # Calling Sim_boot_cov directly here.
    res  <- do.call(Sim_boot_cov, args)
    res$coverage_summary %>% mutate(scenario = nm, .before = 1)
  })

  coverage_table <- bind_rows(all_results)
  message("\n All Scenarios "); print(coverage_table)
  coverage_table
}
```


#  Checking it — Need to inspect One Simulated Dataset Before Running Everything

# Checking one simulated dataset first.
# This makes sure the basic rates look reasonable.

```{r }
set.seed(1)
test_dat <- one_simulation(
  per_diff       = c(0.10, 0.20, 0.40, 0.20, 0.10),   # balanced difficulty
  per_exam_skill = c(0.25, 0.50, 0.25),                # balanced skill
  Hawthorne      = 0, n_examiners = 49, nKQ = 50, nQQ = 50
)

cat("Rows in simulated dataset:", nrow(test_dat), "\n")
cat("Simulated inc_rate :", round(mean(test_dat$Inconclusive), 3), "\n")
cat("Simulated err_rate :", round(mean(test_dat$Error[test_dat$Inconclusive == 0],
                                       na.rm = TRUE), 3), "\n")
cat("Decision distribution:\n"); print(table(test_dat$Decision_D))

# Comparing against the Monte Carlo truth here.
tp <- true_parameters(per_diff       = c(0.10, 0.20, 0.40, 0.20, 0.10),
                      per_exam_skill = c(0.25, 0.50, 0.25), Hawthorne = 0)
cat("\nGround truth (50k MC draws):\n")
cat("  true_inc_rate:", round(tp$true_inc_rate, 3), "\n")
cat("  true_err_rate:", round(tp$true_err_rate, 3), "\n")
cat("(Simulated values should be in the ballpark of these — not identical.)\n")
```


#  Small Bootstrap Validation — Confirming that the whole Pipeline Works Before Full Run

# Running a tiny bootstrap test here first.
# Just making sure the whole pipeline works before the big run.

```{r }
message("Small bootstrap validation (M=5, B=30) — confirming pipeline is working")

small_test <- tryCatch(
  Sim_boot_cov(
    per_diff         = c(0.10, 0.20, 0.40, 0.20, 0.10),   # medium difficulty
    per_exam_skill   = c(0.25, 0.50, 0.25),                # medium skill
    per_quality1     = c(1/3, 1/3, 1/3),
    per_quality2     = rep(0.25, 4),
    Hawthorne        = 0,
    n_examiners      = 10,   # small — just enough to test the machinery
    nKQ              = 10,
    nQQ              = 10,
    mated_prop       = 0.5,
    M                = 5,    # tiny outer loop
    B                = 30,   # tiny bootstrap
    bootstrap_method = "examiner",
    seed             = 1
  ),
  error = function(e) {
    stop("VALIDATION FAILED — Sim_boot_cov threw an error:\n", conditionMessage(e))
  }
)

# Pulling validation metrics here.
val_inc <- small_test$true_parameters$true_inc_rate
val_err <- small_test$true_parameters$true_err_rate
val_cov <- small_test$coverage_summary$coverage_rate

checks <- c(
  "true_inc_rate > 0 and < 1" = (val_inc > 0 && val_inc < 1),
  "true_err_rate > 0 and < 1" = (val_err > 0 && val_err < 1),
  "coverage_rates are finite"  = all(is.finite(val_cov))
)

cat("\n Validation checks\n")
for (nm in names(checks)) {
  cat(sprintf("  [%s] %s\n", if (checks[nm]) "PASS" else "FAIL", nm))
}

if (!all(checks)) {
  stop("VALIDATION FAILED one or more checks above did not pass. ",
       "Inspect true_parameters and coverage_summary before running the full study.")
} else {
  cat("\nAll checks passed. Pipeline is wotrking— proceeding to full run.\n")
  cat(sprintf("  true_inc_rate = %.4f | true_err_rate = %.4f\n", val_inc, val_err))
  cat(sprintf("  Observed coverage rates: inc = %.2f, err = %.2f\n",
              val_cov[1], val_cov[2]))
}
```




# Once the above works:

# Defining the the 36-Scenario Grid

```{r }
# per_diff = proportions for [VEasy, Easy, Norm, Diff, VDiff]
diff_mixes <- list(
  Easy   = c(0.35, 0.35, 0.20, 0.07, 0.03),
  Medium = c(0.10, 0.20, 0.40, 0.20, 0.10),
  Hard   = c(0.03, 0.07, 0.20, 0.35, 0.35)
)

# per_exam_skill = proportions for [Low, Medium, High]
skill_mixes <- list(
  Low    = c(0.60, 0.30, 0.10),
  Medium = c(0.25, 0.50, 0.25),
  High   = c(0.10, 0.30, 0.60)
)

hawthorne_levels <- c(0, 0.15, 0.25, 0.40)

scenario_grid <- expand_grid(
  diff_label  = names(diff_mixes),
  skill_label = names(skill_mixes),
  Hawthorne   = hawthorne_levels
)

cat("Total scenarios:", nrow(scenario_grid), "| Methods: 3 | Total runs:",
    nrow(scenario_grid) * 3, "\n")
print(scenario_grid)
```


# 6. Run All 36 Scenarios × 3 Methods

# Runtime: ~3-5 min per scenario; total ~3-4 hrs. Use cache=TRUE and run overnight.

```{r run-all, cache=TRUE}
M_sim   <- 200   # increase to 500 for final paper
B_sim   <- 300   # increase to 500 for final paper
methods <- c("row", "examiner", "cset")

all_results <- list()

for (i in seq_len(nrow(scenario_grid))) {
  sc <- scenario_grid[i, ]

  for (method in methods) {
    key <- paste0(sc$diff_label, "_", sc$skill_label,
                  "_hw", sc$Hawthorne, "_", method)
    message("\n--- ", key, " ---")

    all_results[[key]] <- Sim_boot_cov(
      per_diff         = diff_mixes[[sc$diff_label]],
      per_exam_skill   = skill_mixes[[sc$skill_label]],
      per_quality1     = c(1/3, 1/3, 1/3),
      per_quality2     = rep(0.25, 4),
      Hawthorne        = sc$Hawthorne,
      n_examiners      = 49, nKQ = 50, nQQ = 50, mated_prop = 0.5,
      M = M_sim, B = B_sim,
      bootstrap_method = method,
      seed = 42
    )
  }
}
```

---

# 7. Compile Results

```{r compile}
results_table <- pmap_dfr(scenario_grid, function(diff_label, skill_label, Hawthorne) {
  map_dfr(methods, function(method) {
    key <- paste0(diff_label, "_", skill_label, "_hw", Hawthorne, "_", method)
    all_results[[key]]$coverage_summary %>%
      mutate(Difficulty = diff_label, Skill = skill_label,
             Hawthorne = Hawthorne, Method = method)
  })
}) %>%
  select(Difficulty, Skill, Hawthorne, Method, statistic,
         true_value, coverage_rate, mean_ci_width, nominal_coverage) %>%
  arrange(Difficulty, Skill, Hawthorne, Method, statistic)

# Show error rate results — primary outcome for the paper
cat("=== Error rate coverage across all scenarios ===\n")
results_table %>% filter(statistic == "err_rate") %>% print(n = Inf)

# Save results so SimulationResults.Rmd can load them without rerunning
saveRDS(results_table, "results_table.rds")
cat("results_table saved to results_table.rds\n")
```

---
