---
title: "simulation function"
output: html_document
---
Goal: simulate a data set with
Examiner ID - each examiner has different skill level 	
Ground Truth: Mated or Non-mated
KQ or QQ
Cset ID - each c set has different difficulty
P (Inconclusive)	Simulated Y results are Identification, lean Identification, Inconclusive, Lean Exclusion, Exclusion 

The data set will include 50 KQ set (25 mated cset, 25 non mated cset) and 50 QQ set(25 mated cset, 25 non mated cset), and 30 examiners
The data set will simulate based on below properties: 
1. difficulty: very easy, easy, medium, difficult, very difficult 
higher difficulty contributes to inconclusive proportion and incorrect direction 
2. Examiner skill: low, high, medium 
higher examiner skill contributes to lower inconclusive proportion and correct direction
3. Evidence quality: A, B, C, D
for KQ set there are always known quanlity with A degree examiner quality
higher quality contributes to lower inconclusive rate
4. Hawthorne effect level: 0 0.1 0.3 0.5
simulate examiner's response based on above influencing factors to following results: Identification, lean Identification, Inconclusive, Lean Exclusion, Exclusion 

one_simulation<-function(per_diff = c(0.25, 0.25,0.25,0.25,0.25), per_exam_skill = c(0.33,0.33,0.33), per_quality=c(0.25, 0.25,0.25,0.25,0.25), Hawthorne = haw_level, )
Use per_diff to set the percentage of difficulty of 5 levels in the simulation; use per_exam_skill to set the percentage of examiners' level in three levels; use per_quality to set the percentage of each quality level in the simulation. 

```{r}
library(dplyr)
library(tidyr)
library(tibble)

logit <- function(p) log(p/(1-p))
invlogit <- function(x) 1/(1+exp(-x))
clip01 <- function(x, lo = 1e-6, hi = 1 - 1e-6) pmin(hi, pmax(lo, x))

difficulty_levels <- c("VeryEasy","Easy","Medium","Difficult","VeryDifficult")
skill_levels <- c("Low","Medium","High")
quality_levels <- c("D","C","B","A") # ordered worst -> best

difficulty_score <- function(x) match(x, difficulty_levels) - 3
skill_score <- function(x) match(x, skill_levels) - 2
quality_score <- function(x) match(x, quality_levels) - 2.5
```


```{r}
simulate_decisions <- function(dat,
                               Hawthorne = 0,
                               seed = 1,
                               # direction model (separate from strength)
                               p_correct_dir_base = 0.80,
                               beta_diff_dir  = -0.35,   # harder -> less correct
                               beta_skill_dir =  0.45,   # higher skill -> more correct
                               beta_qual_dir  =  0.20,   # higher quality -> more correct
                               # combined strength score S
                               beta_diff_strength  = 0.50,  # harder lowers S
                               beta_skill_strength = 0.60,  # higher skill raises S
                               beta_qual_strength  = 0.50,  # higher quality raises S
                               t_insuff = -0.6,             # S < t_insuff => Insuff
                               t_strong =  0.6,             # S >= t_strong => Strong (else Lean)
                               sd_strength_noise = 0.6      # noise on S
) {
  set.seed(seed)
  stopifnot(t_insuff < t_strong)
  stopifnot(Hawthorne >= 0 && Hawthorne <= 1)

  # numeric scores
  d_sc <- difficulty_score(as.character(dat$Difficulty))
  s_sc <- skill_score(as.character(dat$Skill))
  q_sc <- quality_score(as.character(dat$Quality))

  # -----------------------
  # 1) Direction (ID-side vs Excl-side) via correctness
  # -----------------------
  eta_correct <- logit(p_correct_dir_base) +
    beta_diff_dir  * d_sc +
    beta_skill_dir * s_sc +
    beta_qual_dir  * q_sc

  p_correct <- invlogit(eta_correct) |> clip01(0.01, 0.99)
  correct_dir <- rbinom(nrow(dat), 1, p_correct) == 1

  # correct direction means:
  # - Mated => ID-side
  # - Nonmated => Excl-side
  is_mated <- dat$GroundTruth == "Mated"
  id_side <- ifelse(is_mated, correct_dir, !correct_dir)

  # -----------------------
  # 2) Strength score S -> Insuff vs Lean vs Strong
  # -----------------------
  S <- 0 +
    (-beta_diff_strength)  * d_sc +
    ( beta_skill_strength) * s_sc +
    ( beta_qual_strength)  * q_sc +
    rnorm(nrow(dat), 0, sd_strength_noise)

  is_insuff <- S < t_insuff
  is_strong <- S >= t_strong
  is_lean   <- (!is_insuff) & (!is_strong)

  # sanity: each row must be exactly one tier
  stopifnot(all(is_insuff + is_lean + is_strong == 1))

  # -----------------------
  # 3) Map to decisions (Undiscovered)
  # -----------------------
  Decision_U <- character(nrow(dat))
  Decision_U[is_insuff] <- "Insuff"

  idx_nonins <- which(!is_insuff)

  idx_lean <- idx_nonins[is_lean[idx_nonins]]
  if (length(idx_lean) > 0) {
    Decision_U[idx_lean] <- ifelse(id_side[idx_lean], "LeanID", "LeanExcl")
  }

  idx_str <- idx_nonins[is_strong[idx_nonins]]
  if (length(idx_str) > 0) {
    Decision_U[idx_str] <- ifelse(id_side[idx_str], "ID", "Excl")
  }

  # -----------------------
  # 4) Hawthorne effect: flip fraction of Insuff -> definitive
  # -----------------------
  Decision_D <- Decision_U
  inc_idx <- which(Decision_U == "Insuff")
  n_flip <- floor(Hawthorne * length(inc_idx))

  if (n_flip > 0) {
    flip_idx <- sample(inc_idx, n_flip, replace = FALSE)
    def <- Decision_U[Decision_U != "Insuff"]

    if (length(def) > 0) {
      probs <- prop.table(table(def))
      Decision_D[flip_idx] <- sample(
        names(probs),
        size = length(flip_idx),
        replace = TRUE,
        prob = as.numeric(probs)
      )
    }
  }

  dat %>%
    mutate(
      StrengthScore = S,
      P_CorrectDir = p_correct,
      Decision_U = factor(Decision_U, levels = c("ID","LeanID","Insuff","LeanExcl","Excl")),
      Decision_D = factor(Decision_D, levels = c("ID","LeanID","Insuff","LeanExcl","Excl"))
    )
}
```

```{r}
one_simulation <- function(
  per_diff = rep(0.2, 5),
  per_exam_skill = rep(1/3, 3),
  per_quality = rep(0.25, 4),
  Hawthorne = 0,
  seed = 1,
  n_examiners = 30,
  nKQ = 50,
  nQQ = 50
) {
  set.seed(seed)

  stopifnot(length(per_diff) == 5, abs(sum(per_diff) - 1) < 1e-8)
  stopifnot(length(per_exam_skill) == 3, abs(sum(per_exam_skill) - 1) < 1e-8)
  stopifnot(length(per_quality) == 4, abs(sum(per_quality) - 1) < 1e-8)

  # --- csets ---
  cset <- bind_rows(
    tibble(CsetID = paste0("KQ_", sprintf("%03d", 1:nKQ)), ModelType = "KQ"),
    tibble(CsetID = paste0("QQ_", sprintf("%03d", 1:nQQ)), ModelType = "QQ")
  ) %>%
    group_by(ModelType) %>%
    mutate(GroundTruth = c(rep("Mated", 25), rep("Nonmated", 25))) %>%
    ungroup()

  cset$Difficulty <- sample(difficulty_levels, nrow(cset), replace = TRUE, prob = per_diff)

  cset$Quality <- ifelse(
    cset$ModelType == "KQ",
    "A",
    sample(c("A","B","C","D"), nrow(cset), replace = TRUE, prob = per_quality)
  )

  cset <- cset %>%
    mutate(
      ModelType = factor(ModelType, levels = c("KQ","QQ")),
      GroundTruth = factor(GroundTruth, levels = c("Nonmated","Mated")),
      Difficulty = factor(Difficulty, levels = difficulty_levels, ordered = TRUE),
      # IMPORTANT: your quality_levels are D,C,B,A so we convert A/B/C/D into that order
      Quality = factor(Quality, levels = c("D","C","B","A"), ordered = TRUE)
    )

  # --- examiners ---
  exam <- tibble(
    ExaminerID = paste0("E", sprintf("%02d", 1:n_examiners)),
    Skill = sample(skill_levels, n_examiners, replace = TRUE, prob = per_exam_skill)
  ) %>%
    mutate(Skill = factor(Skill, levels = skill_levels, ordered = TRUE))

  # --- responses grid ---
  dat <- tidyr::crossing(exam, cset)

  # --- decisions ---
  simulate_decisions(dat, Hawthorne = Hawthorne, seed = seed + 100)
}
```

```{r}
sim_data <- one_simulation(
  per_diff = c(0.1,0.2,0.4,0.2,0.1),
  per_exam_skill = c(0.3,0.4,0.3),
  per_quality = c(0.25,0.25,0.25,0.25),
  Hawthorne = 0.3,
  seed = 123
)

head(sim_data)
table(sim_data$Decision_U)
table(sim_data$Decision_D)
```

```{r}
# -------------------------------
# Error rates + Bootstrap helpers
# -------------------------------

# Compute FP, FN, overall error, and inconclusive rate
# decision_col should be "Decision_U" or "Decision_D"
compute_error_rates <- function(dat, decision_col = "Decision_D") {
  dec <- dat[[decision_col]]

  fp <- mean(dat$GroundTruth == "Nonmated" & dec %in% c("ID","LeanID"))
  fn <- mean(dat$GroundTruth == "Mated"    & dec %in% c("Excl","LeanExcl"))
  err <- mean(
    (dat$GroundTruth == "Nonmated" & dec %in% c("ID","LeanID")) |
      (dat$GroundTruth == "Mated"  & dec %in% c("Excl","LeanExcl"))
  )
  inc <- mean(dec == "Insuff")

  data.frame(FP = fp, FN = fn, Error = err, Inconclusive = inc)
}

# Generic bootstrap engine for a scalar statistic
# method = "row" | "examiner" | "cset"
bootstrap_ci <- function(dat,
                         stat_fun,
                         method = c("row","examiner","cset"),
                         B = 2000,
                         seed = 1,
                         cluster_var_examiner = "ExaminerID",
                         cluster_var_cset = "CsetID") {
  method <- match.arg(method)
  set.seed(seed)

  n <- nrow(dat)
  vals <- numeric(B)

  if (method == "row") {
    for (b in 1:B) {
      idx <- sample.int(n, n, replace = TRUE)
      vals[b] <- stat_fun(dat[idx, , drop = FALSE])
    }
  }

  if (method == "examiner") {
    clusters <- unique(dat[[cluster_var_examiner]])
    idx_by <- split(seq_len(n), dat[[cluster_var_examiner]])
    for (b in 1:B) {
      samp <- sample(clusters, length(clusters), replace = TRUE)
      idx <- unlist(idx_by[samp], use.names = FALSE)
      vals[b] <- stat_fun(dat[idx, , drop = FALSE])
    }
  }

  if (method == "cset") {
    clusters <- unique(dat[[cluster_var_cset]])
    idx_by <- split(seq_len(n), dat[[cluster_var_cset]])
    for (b in 1:B) {
      samp <- sample(clusters, length(clusters), replace = TRUE)
      idx <- unlist(idx_by[samp], use.names = FALSE)
      vals[b] <- stat_fun(dat[idx, , drop = FALSE])
    }
  }

  ci <- quantile(vals, c(0.025, 0.975), na.rm = TRUE)

  list(
    method = method,
    B = B,
    boot_values = vals,
    mean = mean(vals, na.rm = TRUE),
    sd = sd(vals, na.rm = TRUE),
    lo = unname(ci[1]),
    hi = unname(ci[2])
  )
}

# ---------------------------------------------------------
# Combined function: simulate + bootstrap CI for error rate
# ---------------------------------------------------------
simulate_and_bootstrap <- function(
  bootstrap_method = c("row","examiner","cset"),
  decision_col = "Decision_D",
  B = 2000,
  seed = 123,

  # pass-through args to one_simulation()
  per_diff = rep(0.2, 5),
  per_exam_skill = rep(1/3, 3),
  per_quality = rep(0.25, 4),
  Hawthorne = 0,
  n_examiners = 30,
  nKQ = 50,
  nQQ = 50
) {
  bootstrap_method <- match.arg(bootstrap_method)

  # 1) simulate dataset
  dat <- one_simulation(
    per_diff = per_diff,
    per_exam_skill = per_exam_skill,
    per_quality = per_quality,
    Hawthorne = Hawthorne,
    seed = seed,
    n_examiners = n_examiners,
    nKQ = nKQ,
    nQQ = nQQ
  )

  # 2) point estimates (FP/FN/Error/Inc)
  point <- compute_error_rates(dat, decision_col = decision_col)

  # 3) bootstrap CI for overall Error rate (scalar)
  stat_fun <- function(d) compute_error_rates(d, decision_col = decision_col)$Error

  boot <- bootstrap_ci(
    dat = dat,
    stat_fun = stat_fun,
    method = bootstrap_method,
    B = B,
    seed = seed + 999
  )

  # 4) return everything
  list(
    data = dat,
    decision_col = decision_col,
    point_estimates = point,
    bootstrap = boot
  )
}
```

