---
title: "Part 3 – Simulation Results: Figures and Conclusions"
output:
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

---

# 0. Libraries

```{r libraries}
library(dplyr)
library(tidyr)
library(ggplot2)
library(scales)
library(purrr)
```

---

# 1. Load Results

```{r load-results}
results_table <- readRDS("results_table.rds")

cat("Scenarios loaded:", nrow(results_table) / 2, "\n")   # /2 because inc + err rows
cat("Methods:", paste(unique(results_table$Method), collapse = ", "), "\n")
cat("Difficulty levels:", paste(unique(results_table$Difficulty), collapse = ", "), "\n")
cat("Skill levels:", paste(unique(results_table$Skill), collapse = ", "), "\n")
cat("Hawthorne levels:", paste(sort(unique(results_table$Hawthorne)), collapse = ", "), "\n")

# Quick sanity check: confirm no missing coverage values
n_missing <- sum(is.na(results_table$coverage_rate))
if (n_missing > 0) warning(n_missing, " missing coverage_rate values found.")
```

---

# 2. Figure 1 — Coverage by method (no Hawthorne effect)

**What to look for:**
- Does any method stay reliably near 0.95 across all Difficulty × Skill combinations?
- Does the Naive (row) bootstrap fall below 0.95? → confirms real clustering exists
- Which clustered method tracks the dashed line better? → reveals dominant clustering level

```{r fig1, fig.width=10, fig.height=5}
results_table %>%
  filter(Hawthorne == 0, statistic == "err_rate") %>%
  mutate(Method = recode(Method,
                         "row"      = "Naive (row)",
                         "examiner" = "Examiner-clustered",
                         "cset"     = "Cset-clustered")) %>%
  ggplot(aes(x = Skill, y = coverage_rate, colour = Method, group = Method)) +
  geom_hline(yintercept = 0.95, linetype = "dashed", colour = "grey40", linewidth = 0.8) +
  geom_line(linewidth = 1) +
  geom_point(size = 3) +
  facet_wrap(~Difficulty, ncol = 3) +
  scale_y_continuous(limits = c(0.5, 1.0), labels = percent) +
  scale_colour_manual(values = c("Naive (row)"         = "#e41a1c",
                                 "Examiner-clustered"  = "#377eb8",
                                 "Cset-clustered"      = "#4daf4a")) +
  labs(title    = "Figure 1: Error-rate CI coverage by bootstrap method (Hawthorne = 0)",
       subtitle = "Dashed line = 95% nominal target. Values below line = CIs too narrow.",
       x = "Examiner skill mix", y = "Empirical coverage", colour = NULL) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom")
```

---

# 3. Figure 2 — Coverage vs. Hawthorne delta

**What to look for:**
- Does coverage degrade as Hawthorne increases? → bootstrap not adjusting for inc-rate shift
- Is one method more robust to Hawthorne than the others?

```{r fig2, fig.width=11, fig.height=7}
results_table %>%
  filter(statistic == "err_rate") %>%
  mutate(Method = recode(Method,
                         "row"      = "Naive",
                         "examiner" = "Examiner",
                         "cset"     = "Cset")) %>%
  ggplot(aes(x = factor(Hawthorne), y = coverage_rate,
             colour = Method, group = Method)) +
  geom_hline(yintercept = 0.95, linetype = "dashed", colour = "grey40", linewidth = 0.7) +
  geom_line(linewidth = 0.9) +
  geom_point(size = 2.5) +
  facet_grid(Skill ~ Difficulty) +
  scale_y_continuous(limits = c(0.5, 1.0), labels = percent) +
  scale_colour_manual(values = c("Naive"    = "#e41a1c",
                                 "Examiner" = "#377eb8",
                                 "Cset"     = "#4daf4a")) +
  labs(title    = "Figure 2: How Hawthorne delta affects error-rate coverage",
       subtitle = "Each panel = one Difficulty × Skill combination",
       x = "Hawthorne delta", y = "Empirical coverage", colour = "Method") +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom")
```

---

# 4. Figure 3 — CI width vs. Hawthorne delta

**What to look for:**
- Coverage alone doesn't determine the best method — a very wide CI always covers but is useless.
- Best method: coverage ≈ 0.95 AND narrowest CI width.

```{r fig3, fig.width=11, fig.height=7}
results_table %>%
  filter(statistic == "err_rate") %>%
  mutate(Method   = recode(Method,
                           "row"      = "Naive",
                           "examiner" = "Examiner",
                           "cset"     = "Cset"),
         Scenario = paste0(Difficulty, " / ", Skill)) %>%
  ggplot(aes(x = factor(Hawthorne), y = mean_ci_width,
             colour = Method, group = Method)) +
  geom_line(linewidth = 0.9) +
  geom_point(size = 2.5) +
  facet_wrap(~Scenario, ncol = 3) +
  scale_colour_manual(values = c("Naive"    = "#e41a1c",
                                 "Examiner" = "#377eb8",
                                 "Cset"     = "#4daf4a")) +
  labs(title    = "Figure 3: Mean 95% CI width for error rate",
       subtitle = "Narrower = more precise. Best method: coverage ≈ 0.95 AND narrowest CI.",
       x = "Hawthorne delta", y = "Mean CI width", colour = "Method") +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom")
```

---

# 5. Figure 4 — Full heatmap (all 36 scenarios, all methods)

**What to look for:**
- Green = well-calibrated (coverage ≈ 95%)
- Red = undercoverage (CIs too narrow — bootstrap ignores real dependence)
- Yellow = acceptable but not ideal

```{r fig4, fig.width=14, fig.height=7}
results_table %>%
  filter(statistic == "err_rate") %>%
  mutate(
    Scenario = paste0(Difficulty, " / ", Skill),
    Method   = recode(Method,
                      "row"      = "Naive",
                      "examiner" = "Examiner",
                      "cset"     = "Cset")
  ) %>%
  ggplot(aes(x = Method, y = Scenario, fill = coverage_rate)) +
  geom_tile(colour = "white", linewidth = 0.6) +
  geom_text(aes(label = percent(coverage_rate, accuracy = 1)),
            size = 3.2, fontface = "bold") +
  facet_wrap(~Hawthorne, ncol = 4,
             labeller = labeller(Hawthorne = function(x) paste0("Hawthorne δ = ", x))) +
  scale_fill_gradient2(low = "#d73027", mid = "#ffffbf", high = "#1a9850",
                       midpoint = 0.95, limits = c(0.5, 1.0),
                       labels = percent, name = "Coverage") +
  labs(title    = "Figure 4: Bootstrap coverage (error rate) — all 36 scenarios",
       subtitle = "Green = ~95% nominal. Red = undercoverage. Yellow = borderline.",
       x = NULL, y = NULL) +
  theme_minimal(base_size = 11) +
  theme(axis.text.x = element_text(angle = 25, hjust = 1),
        legend.position = "right")
```

---

# 6. Conclusions

## 6a. Which method wins most often?

```{r conclusion-winner}
cat("=== Which method achieves closest-to-nominal coverage most often? ===\n")
results_table %>%
  filter(statistic == "err_rate") %>%
  group_by(Difficulty, Skill, Hawthorne) %>%
  slice_max(coverage_rate, with_ties = FALSE) %>%
  ungroup() %>%
  count(Method, name = "n_scenarios_best") %>%
  arrange(desc(n_scenarios_best)) %>%
  print()
```

## 6b. Mean coverage and CI width by method

```{r conclusion-summary}
cat("=== Mean coverage and CI width by method (error rate) ===\n")
results_table %>%
  filter(statistic == "err_rate") %>%
  group_by(Method) %>%
  summarise(
    Mean_Coverage = mean(coverage_rate),
    SD_Coverage   = sd(coverage_rate),
    Min_Coverage  = min(coverage_rate),
    Mean_Width    = mean(mean_ci_width),
    .groups = "drop"
  ) %>%
  arrange(desc(Mean_Coverage)) %>%
  print()
```

## 6c. Effect of Hawthorne delta on coverage

```{r conclusion-hawthorne}
cat("=== Mean coverage by Hawthorne level, by method (error rate) ===\n")
results_table %>%
  filter(statistic == "err_rate") %>%
  group_by(Hawthorne, Method) %>%
  summarise(Mean_Coverage = mean(coverage_rate), .groups = "drop") %>%
  pivot_wider(names_from = Method, values_from = Mean_Coverage) %>%
  arrange(Hawthorne) %>%
  print()
```

## 6d. Inconclusive rate (secondary outcome)

```{r conclusion-inc-rate}
cat("=== Mean coverage and CI width by method (inconclusive rate) ===\n")
results_table %>%
  filter(statistic == "inc_rate") %>%
  group_by(Method) %>%
  summarise(Mean_Coverage = mean(coverage_rate),
            SD_Coverage   = sd(coverage_rate),
            Min_Coverage  = min(coverage_rate),
            Mean_Width    = mean(mean_ci_width),
            .groups = "drop") %>%
  arrange(desc(Mean_Coverage)) %>%
  print()
```

## 6e. Plain-English Conclusion

```{r conclusion-narrative}
best_method <- results_table %>%
  filter(statistic == "err_rate") %>%
  group_by(Difficulty, Skill, Hawthorne) %>%
  slice_max(coverage_rate, with_ties = FALSE) %>%
  ungroup() %>%
  count(Method) %>%
  slice_max(n) %>%
  pull(Method)

avg_cov <- results_table %>%
  filter(statistic == "err_rate") %>%
  group_by(Method) %>%
  summarise(cov = mean(coverage_rate), .groups = "drop") %>%
  deframe()

cat("\n=== PLAIN-ENGLISH CONCLUSION ===\n\n")
cat(sprintf(
"Across all 36 scenarios (3 difficulty mixes × 3 skill mixes × 4 Hawthorne levels),
the %s bootstrap achieved the closest-to-nominal 95%% coverage most frequently.

Average empirical coverage:
  Row (naive):          %.1f%%
  Examiner-clustered:   %.1f%%
  Cset-clustered:       %.1f%%

These results indicate that the dominant clustering level drives the dependence
structure of the data, and that naive row resampling may fail to capture this
structure. The recommended bootstrap method for reporting error rate confidence
intervals in future forensic bullet studies is the %s bootstrap.

Note: if coverage is similar between two clustered methods but one produces narrower
CIs, that method should be preferred for practical reporting.
",
  best_method,
  avg_cov["row"]      * 100,
  avg_cov["examiner"] * 100,
  avg_cov["cset"]     * 100,
  best_method
))
```

---

# 7. Session Info

```{r session-info}
sessionInfo()
```
