
---
title: "Code for Proposal"
output: html_document
---

```{r}
library(readxl)
library(dplyr)
library(stringr)
library(purrr)  
```

## 1) Import data

```{r}
file_path <- "bullets_2024.xlsx"

kq_data   <- read_excel(file_path, sheet = "KQ responses (n=1575)")
qq_data   <- read_excel(file_path, sheet = "QQ responses (n=1581)")
cset_data <- read_excel(file_path, sheet = "Cset (n=1240)")
```

## 2) Clean + combine into one response table

```{r}
phase_label <- "Primary (Baseline)"

kq <- kq_data %>%
  filter(Phase == phase_label) %>%
  mutate(
    Decision   = if_else(K01_Q1value == "NoValue", "NoValue", K08_Conclusion),
    Comparison = "KQ"
  ) %>%
  select(AnonID, Cset, Mating, Decision, Comparison)

qq <- qq_data %>%
  filter(Phase == phase_label) %>%
  mutate(
    Decision   = if_else(Q01_Q1value == "NoValue" | Q02_Q2value == "NoValue", "NoValue", Q08_Conclusion),
    Comparison = "QQ"
  ) %>%
  select(AnonID, Cset, Mating, Decision, Comparison)

cset <- cset_data %>%
  select(Cset, Type, `Cset Category (Detailed)`, `Cset Quality (voted)`) %>%
  rename(
    Category    = `Cset Category (Detailed)`,
    CsetQuality = `Cset Quality (voted)`
  )

responses <- bind_rows(kq, qq) %>%
  left_join(cset, by = "Cset") %>%
  mutate(
    Category = str_squish(Category),
    Decision = factor(Decision, levels = c("ID", "LeanID", "Insuff", "NoValue", "LeanExcl", "Excl"))
  )
```

## 3) Define FP / FN / Inconclusive + compute baseline rates

```{r}
classify_calls <- function(df) {
  df %>%
    mutate(
      truth = if_else(Mating == "Mated", "SameSource", "DifferentSource"),
      call_type = case_when(
        Decision %in% c("ID", "LeanID")         ~ "ID",
        Decision %in% c("Excl", "LeanExcl")     ~ "Excl",
        Decision %in% c("Insuff", "NoValue")    ~ "Inconclusive",
        TRUE ~ NA_character_
      ),
      is_fp = (truth == "DifferentSource" & call_type == "ID"),
      is_fn = (truth == "SameSource"      & call_type == "Excl"),
      is_inconclusive = (call_type == "Inconclusive")
    )
}

calc_rates <- function(df) {
  df2 <- classify_calls(df)

  n_diff <- sum(df2$truth == "DifferentSource", na.rm = TRUE)
  n_same <- sum(df2$truth == "SameSource",      na.rm = TRUE)

  tibble(
    n = nrow(df2),
    fp = sum(df2$is_fp, na.rm = TRUE),
    fn = sum(df2$is_fn, na.rm = TRUE),
    inconclusive = sum(df2$is_inconclusive, na.rm = TRUE),

    fp_rate = if_else(n_diff > 0, fp / n_diff, NA_real_),
    fn_rate = if_else(n_same > 0, fn / n_same, NA_real_),

    inconclusive_rate_overall = mean(df2$is_inconclusive, na.rm = TRUE),
    inconclusive_rate_same    = mean(df2$is_inconclusive[df2$truth == "SameSource"], na.rm = TRUE),
    inconclusive_rate_diff    = mean(df2$is_inconclusive[df2$truth == "DifferentSource"], na.rm = TRUE)
  )
}

baseline_rates <- calc_rates(responses)
baseline_rates
```

## 4) Bootstrap confidence intervals (3 methods)

```{r}
boot_ci_percentile <- function(x, alpha = 0.05) {
  stats::quantile(x, probs = c(alpha/2, 1 - alpha/2), na.rm = TRUE)
}

run_bootstrap <- function(df, B, resample_fun, stat_fun) {
  replicate(B, stat_fun(resample_fun(df)))
}

# (1) naive: resample rows (assumes independence)
resample_rows <- function(df) {
  df[sample.int(nrow(df), nrow(df), replace = TRUE), , drop = FALSE]
}

# (2)/(3) clustered: resample clusters (preserves dependence within examiner or item)
resample_cluster <- function(df, cluster_col) {
  clusters <- unique(df[[cluster_col]])
  sampled  <- sample(clusters, length(clusters), replace = TRUE)
  map_dfr(sampled, ~ df[df[[cluster_col]] == .x, , drop = FALSE])
}

set.seed(1)
boot_fp_naive <- run_bootstrap(responses, B = 500, resample_fun = resample_rows,
                               stat_fun = function(d) calc_rates(d)$fp_rate)
ci_fp_naive <- boot_ci_percentile(boot_fp_naive)

set.seed(2)
boot_fp_examiner <- run_bootstrap(responses, B = 500,
                                  resample_fun = function(d) resample_cluster(d, "AnonID"),
                                  stat_fun = function(d) calc_rates(d)$fp_rate)
ci_fp_examiner <- boot_ci_percentile(boot_fp_examiner)

set.seed(3)
boot_fp_item <- run_bootstrap(responses, B = 500,
                              resample_fun = function(d) resample_cluster(d, "Cset"),
                              stat_fun = function(d) calc_rates(d)$fp_rate)
ci_fp_item <- boot_ci_percentile(boot_fp_item)

list(
  fp_ci_naive    = ci_fp_naive,
  fp_ci_examiner = ci_fp_examiner,
  fp_ci_item     = ci_fp_item
)
```

## 5) Hawthorne effect: flip some conclusive calls to Inconclusive

```{r}
add_hawthorne <- function(df, p_discovered = 0.191, delta = 0.25, seed = NULL) {
  if (!is.null(seed)) set.seed(seed)

  df2 <- classify_calls(df) %>%
    mutate(
      discovered = rbinom(n(), 1, p_discovered),
      conclusive = call_type %in% c("ID", "Excl")
    )

  flip <- (df2$discovered == 1 & df2$conclusive & runif(nrow(df2)) < delta)

  df2$Decision <- as.character(df2$Decision)
  df2$Decision[flip] <- "Insuff"
  df2$Decision <- factor(df2$Decision, levels = levels(df$Decision))

  df2 %>% select(names(df))
}

df_h <- add_hawthorne(responses, p_discovered = 0.191, delta = 0.25, seed = 4)

list(
  baseline = calc_rates(responses),
  hawthorne = calc_rates(df_h)
)
```

What was being done:

Using the cleaned 2024 Bullet Black Box Study data, we combined KQ and QQ baseline responses into a single dataset and computed false positive (FP), false negative (FN), and inconclusive rates using ground truth from the Mating variable(Mated/NonMated.

We then estimated uncertainty in the FP rate using three bootstrap methods: a naive row-level bootstrap, an examiner-clustered bootstrap (resampling by AnonID), and an item-clustered bootstrap (resampling by Cset).

The naive and item-clustered confidence intervals were relatively similar and narrower, while the examiner-clustered interval was substantially wider, indicating meaningful examiner-level dependence and suggesting that naive resampling may underestimate uncertainty.

Finally, we simulated a Hawthorne (test-awareness) effect by converting a fraction of conclusive decisions into inconclusive calls, which increased the overall inconclusive rate and slightly reduced FP and FN rates, reflecting a shift toward more conservative decision-making under awareness conditions.










